### 2024-03-15 paper/paper.tex
paper

%%
%% This is file `sample-sigplan.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `all,proceedings,bibtex,sigplan')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigplan.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%%
%%  Uncomment \acmBooktitle if the title of the proceedings is different
%%  from ``Proceedings of ...''!
%%
%%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%%  June 03--05, 2018, Woodstock, NY}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{The Name of the Title Is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Mukesh Tiwari}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}

\author{Berry Schonemark}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}}

\author{Bas Spitters}
\affiliation{%
  \institution{The Kumquat Consortium}
  \city{New York}
  \country{USA}}
\email{jpkumquat@consortium.net}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Tiwari et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Abstract goes here
\end{abstract}

\begin{CCSXML}
<ccs2012>
  <concept>
      <concept_id>10002978.10002986.10002990</concept_id>
      <concept_desc>Security and privacy~Logic and verification</concept_desc>
      <concept_significance>500</concept_significance>
      </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Logic and verification}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Sigma Protocol, Formal Verification, Coq, Cryptography, Zero-Knowledge Proof}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
\begin{itemize}
  \item Explain zero-knowledge proofs (completeness, soundness, zero-knowledge)
  \item Explain sigma protocols (completeness, special-soundness, honest-verifier zero-knowledg) 
  and mention about the Schnorr protocol
  \item Our contribution
  \item Explain the Schnorr protocol
  \item Explain Parallel, And, Eq, Or, and NEQ relations (also explain that 
  most of the formalisation has worked on And and Or relations)
\end{itemize}
Zero-knowledge proofs are a class of cryptographic protocols that allow a
prover to convince a verifier that a statement is true without revealing 
any information about the statement itself. 
Zero-knowledge proofs are possible for all problems in the $NP$ complexity class. 
$NP$ includes problems where a proof of membership can be efficiently 
verified in polynomial time. In NP, a witness (denoted as $w$) is a 
polynomial-length piece of evidence that allows quick
verification (in polynomial time) that a given statement $s$ 
belongs to the language. This verification process can be represented 
using a binary relation $R$ between the set of statements (S) and the 
set of witnesses ($W$), where $(s, w) \in R$ if the witness $w$ 
demonstrates that the statement $s$ is in the language.

Sigma protocols were first defined by Ronald Cramer [18],
they are a particularly simple and efficient kind of zero-
knowledge proof and have seen wide deployment; they re-
main a leading kind of proof both in terms of simplicity and
deployment but recent advances in succinct zero-knowledge
proofs [26] offer greater efficiency. The first efficient sigma
protocol was introduced by Schnorr in [38], several years
before the class was defined.

Sigma protocols are a class of cryptographic protocols that are used to prove the 
knowledge of a witness for a given statement.

They are used in various cryptographic 
applications such as identification, authentication, and zero-knowledge proofs. 
The security of these protocols is based on the hardness of certain mathematical 
problems such as the discrete logarithm problem. Amongst sigma protocols, 
one of the most well-known protocols is the Schnorr protocol. In this 
paper, we present a formal verification of the Schnorr protocol in the
Coq proof assistant.

In this paper, we present a 
formal verification of a sigma protocol in the Coq proof assistant. We use 
the Fiat-Crypto library to implement the protocol and prove its security 
properties. Our work is based on the work of \cite{fiat-crypto} and \cite{pok}.

\section{Sigma Protocols}

  Explain here the definition of Sigma Protocols and the Schnorr protocol.

  \subsection{Parallel Composition}
  Explain the parallel composition of sigma protocols.

  \subsection{And Composition}
  Explain the and composition of sigma protocols.

  \subsection{Or Composition}
  Explain the or composition of sigma protocols.

  \subsection{Equality Composition}
  Explain the equality composition of sigma protocols.

  \subsection{Inequality Composition}
  Explain the inequality composition of sigma protocols.

\section{Formal Verification of Sigma Protocols}

\section{Web Assembly and Rust from the Coq Formalisation}
  Bas Spitter

\section{Case Studies}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios and Belenois voting systems.

\section{Related Work}
  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.

\section{Conclusion, Future Work, and Limitations}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

%%
%% If your work has an appendix, this is the place to put it.
%\appendix

\end{document}
\endinput
%%
%% End of file `sample-sigplan.tex'.

### 2024-03-22 paper/paper.tex
Started writing paper

@@
 \affiliation{%
- \institution{Rajiv Gandhi University}
- \streetaddress{Rono-Hills}
- \city{Doimukh}
- \state{Arunachal Pradesh}
- \country{India}}
+ \institution{Swansea University}
+ \country{United Kingdom}}
+ \email{mukesh.tiwari@swansea.ac.uk}
 
-\author{Berry Schonemark}
+\author{Berry Schoenmakers}
 \affiliation{%
-  \institution{Tsinghua University}
-  \streetaddress{30 Shuangqing Rd}
-  \city{Haidian Qu}
-  \state{Beijing Shi}
-  \country{China}}
+  \institution{TU Eindhoven, Eindhoven}
+  \country{The Netherlands}}
+  \email{l.a.m.schoenmakers@tue.nl}
 
@@
 \affiliation{%
-  \institution{The Kumquat Consortium}
-  \city{New York}
-  \country{USA}}
-\email{jpkumquat@consortium.net}
+  \institution{Aarhus University}
+  \country{Denmark}}
+\email{spitters@cs.au.dk}
 
@@
 
+\section{How to pitch this paper and What is the unique selling point of our work?}
+Our Coq formalisation can be used at front-end to generate Web Assembly code and 
+Rust code at the back-end. Contrary to the existing work, our formalisation
+does not write the same code twice. But sigma protocols are arcane and has 
+been formalised couple of times before so why another formalisation?
+None of the formalisation has been able to extract the code to executable code 
+and one that was able to do so did not reason about probabilities in an intuitive way.
+Moreover, that work was just geared towards verifying a transcript rather than
+constructing it. Also, recently ZKP community started a movement to 
+formalise the Sigma protocols. We also demonstrates the 
+applicability of our formalisation by encoding Helios cryptographic protocols
+in our formalisation.
+
 \section{Introduction}
+Despite the recent growth and popularity of zero-knowledge succinct 
+argument of knowledge (ZKSNARK), Sigma protocols remain a
+leading cryptographic proof system in privacy-preserving voting systems. 
+Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
+Moreover, recently ZKP community started a movement to standardise
+the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
+other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
+they possess some knowledge without revealing anything else about the knowledge itself.  
+More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
+that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
+Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
+assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
+first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
+Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
+sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
+Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
+also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
+and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol and 
+its $n$ NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
+much use of Okamoto protocol in the privacy-preserving voting systems  (\textbf{Berry: does it sound okay?}), 
+at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
+but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
+Web Assembly and Rust.
+
+There are numerous implementations of Sigma protocols in various languages, 
+e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
+However, there are two main issues with these implementations: (i)  
+the same code is written twice 
+once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
+especially in privacy-preserving voting systems such as Helios, SwissPost, and 
+(ii) none of these implementations offer any formal guarantees about the correctness of the code.
+Given the importance of Sigma protocols in privacy-preserving voting systems,
+it has been formalised couple of times before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
+\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
+pen-and-paper proofs of Sigma protocols into theorem provers, and not extracting an executable code.
+On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
+formalisation but it is mostly geared towards verifying an Helios election transcript, 
+rather than constructing the primitives to conduct an election. Moreover, 
+it lacks many primitives and does not reason about probabilities in an intuitive way.
+
+In this paper, we present a formal verification of Sigma protocols in the Coq proof assistant that 
+can be used to generate Web Assembly code at the front-end and Rust code at the back-end. 
+We use our formalisation to model the cryptographic protocols implemented in Helios voting systems.
+
+\textbf{We need to explain why formal verification is important in the context of voting systems.}
+
 \begin{itemize}
@@
 \end{itemize}
+
 Zero-knowledge proofs are a class of cryptographic protocols that allow a
@@
 
-Sigma protocols were first defined by Ronald Cramer [18],
-they are a particularly simple and efficient kind of zero-
-knowledge proof and have seen wide deployment; they re-
-main a leading kind of proof both in terms of simplicity and
-deployment but recent advances in succinct zero-knowledge
-proofs [26] offer greater efficiency. The first efficient sigma
-protocol was introduced by Schnorr in [38], several years
-before the class was defined.
-
 Sigma protocols are a class of cryptographic protocols that are used to prove the 
@@
 Coq proof assistant.
-
-In this paper, we present a 
-formal verification of a sigma protocol in the Coq proof assistant. We use 
-the Fiat-Crypto library to implement the protocol and prove its security 
-properties. Our work is based on the work of \cite{fiat-crypto} and \cite{pok}.
 
@@
   We use our formalisation to model the Cryptographic protocols implemented in 
-  Helios and Belenois voting systems.
+  Helios voting systems.
 

### 2024-04-08 paper/paper.tex
paper and removed locate

@@
 also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
-and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol and 
-its $n$ NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
-much use of Okamoto protocol in the privacy-preserving voting systems  (\textbf{Berry: does it sound okay?}), 
+and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
+for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
+much use of Okamoto protocol in the privacy-preserving voting systems, 
 at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,

### 2024-04-24 paper/paper.tex
text added

@@
 \begin{abstract}
-  Abstract goes here
+  Despite the recent growth of zero-knowledge succinct argument 
+  of knowledge (ZKSNARK) in cryptocurrencies, 
+  sigma protocol remains a popular choice in electronic voting to maintain privacy 
+  and verifiability of elections and still used in Helios, Belenois, and SwissPost voting systems. 
+  However, the existing implementations of sigma protocol are not formally verified and 
+  therefore offer no security guarantees. \textbf{Double check this and its purpose: Moreover, 
+  the same code is written twice, once for the front-end and once for the back-end}.
+  In this paper, we present a formal verification of sigma protocol in the Coq proof assistant. 
+  We prove that our formalisation is (special) sound, complete, and (honest verifier) 
+  zero-knowledge. Moreover, 
+  we compile our Coq formalisation to WebAssembly code and Rust code, and 
+  thereby solve the problem of writing the same code twice, once for the 
+  front-end and once for the back-end. We demonstrate the applicability of our
+  formalisation by encoding the cryptographic protocols implemented in 
+  Helios voting systems. Our long terms goal is to provide a verified
+  cryptographic library that can be readily used in 
+  privacy-preserving voting systems.
+
 \end{abstract}
@@
 Despite the recent growth and popularity of zero-knowledge succinct 
-argument of knowledge (ZKSNARK), Sigma protocols remain a
+argument of knowledge (ZKSNARK), sigma protocol remains a
 leading cryptographic proof system in privacy-preserving voting systems. 
-Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
+Sigma protocols are used in Helios, Belenois, and SwissPost voting 
+systems (\textbf{Look for more examples}). 
 Moreover, recently ZKP community started a movement to standardise
-the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
+the Sigma protocols.
+
+One of the main reasons for the popularity of sigma protocols in 
+privacy-preserving voting systems is their simplicity and well-understood
+security.
+
+Sigma protocols are a special case of
+zero-knowledge proofs where the verifier is assumed to be honest. Sigma protocols
+allow a prover to convince a verifier that they possess some knowledge without
+revealing anything else about the knowledge itself. Sigma protocols are used in
+
+\textbf{Introduce here that sigma protocols are efficient and simple and all 
 other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 

### 2024-05-09 paper/paper.tex
Text

--- 2024-04-08 paper/paper.tex
@@
 \acmISBN{978-1-4503-XXXX-X/18/06}
+
+%% get rid of this for the final version
+\usepackage{todonotes}
+\usepackage{listingsutf8}
+\setlength {\marginparwidth }{2cm} %This is for todod
+\usepackage{tikz}
+\usetikzlibrary{positioning}
+\usepackage{cryptocode}
+\usepackage{lstcoq}
+\usepackage[utf8]{inputenc}
+%% End of get rid of this for the final version
 
@@
 \begin{abstract}
-  Abstract goes here
+  Despite the recent growth of zero-knowledge succinct argument 
+  of knowledge (ZKSNARK) in cryptocurrencies, 
+  sigma protocol remains a popular choice in electronic voting to maintain privacy 
+  and verifiability of elections and still used in prominent e-voting systems such as 
+  Helios, Belenois, and SwissPost \textbf{More examples}. However, 
+  the existing implementations of sigma protocol have two 
+  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
+  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
+  and (ii) none of these implementations offer any security guarantees. 
+  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant. 
+  We prove that our implementation is (special) sound, complete, and 
+  (honest verifier) zero-knowledge. Moreover, 
+  we compile our Coq formalisation to WebAssembly and Rust, and 
+  thereby solve the problem of writing the same code twice. 
+  We demonstrate the applicability of our
+  formalisation by encoding the cryptographic protocols implemented in 
+  Helios, Belenois, and SwissPost voting systems. 
+  Our long terms goal is to provide a verified cryptographic library that can be 
+  readily used in privacy-preserving voting systems.
+
 \end{abstract}
@@
 \section{How to pitch this paper and What is the unique selling point of our work?}
-Our Coq formalisation can be used at front-end to generate Web Assembly code and 
-Rust code at the back-end. Contrary to the existing work, our formalisation
-does not write the same code twice. But sigma protocols are arcane and has 
+Our Coq formalisation can be used at front-end (WebAssembly code) and 
+back-end (Rust). Contrary to the existing work, our formalisation
+does not write the same code twice. But sigma protocol is arcane and has 
 been formalised couple of times before so why another formalisation?
@@
 constructing it. Also, recently ZKP community started a movement to 
-formalise the Sigma protocols. We also demonstrates the 
+formalise the sigma protocols. We also demonstrates the 
 applicability of our formalisation by encoding Helios cryptographic protocols
 in our formalisation.
-
-\section{Introduction}
-Despite the recent growth and popularity of zero-knowledge succinct 
-argument of knowledge (ZKSNARK), Sigma protocols remain a
-leading cryptographic proof system in privacy-preserving voting systems. 
-Sigma protocols are used in Helios, Belenois, and SwissPost voting systems (\textbf{Look for more examples}). 
-Moreover, recently ZKP community started a movement to standardise
-the Sigma protocols. \textbf{Introduce here that sigma protocols are efficient and simple and all 
-other details about sigma protocols.} Sigma protocols allow a prover to convince a verifier that 
-they possess some knowledge without revealing anything else about the knowledge itself.  
-More formally, for a given relation $R$ and a statement $x$, the prover convinces the verifier
-that they posses a witness $w$ such that ($x$, $w$) $\in$ $R$. We would like to stress that
-Sigma protocols are a special case of zero-knowledge proofs where the verifier is 
-assumed to be honest. Sigma protocols were first defined by Ronald Cramer \cite{cramer1996modular} and the 
-first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
-Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
-sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, SwissPost, etc. 
-Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
-also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
-and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
-for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
-much use of Okamoto protocol in the privacy-preserving voting systems, 
-at least in the existing voting systems. Ideally, we could have abstracted the sigma protocols and their composition in a generic way,
-but we decided to focus on the Schnorr protocol and its composition to ensure a nice APIs in 
-Web Assembly and Rust.
-
-There are numerous implementations of Sigma protocols in various languages, 
-e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
-However, there are two main issues with these implementations: (i)  
-the same code is written twice 
-once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
-especially in privacy-preserving voting systems such as Helios, SwissPost, and 
-(ii) none of these implementations offer any formal guarantees about the correctness of the code.
-Given the importance of Sigma protocols in privacy-preserving voting systems,
-it has been formalised couple of times before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
-\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
-pen-and-paper proofs of Sigma protocols into theorem provers, and not extracting an executable code.
-On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
-formalisation but it is mostly geared towards verifying an Helios election transcript, 
-rather than constructing the primitives to conduct an election. Moreover, 
-it lacks many primitives and does not reason about probabilities in an intuitive way.
-
-In this paper, we present a formal verification of Sigma protocols in the Coq proof assistant that 
-can be used to generate Web Assembly code at the front-end and Rust code at the back-end. 
-We use our formalisation to model the cryptographic protocols implemented in Helios voting systems.
 
@@
 
-Zero-knowledge proofs are a class of cryptographic protocols that allow a
-prover to convince a verifier that a statement is true without revealing 
-any information about the statement itself. 
-Zero-knowledge proofs are possible for all problems in the $NP$ complexity class. 
-$NP$ includes problems where a proof of membership can be efficiently 
-verified in polynomial time. In NP, a witness (denoted as $w$) is a 
-polynomial-length piece of evidence that allows quick
-verification (in polynomial time) that a given statement $s$ 
-belongs to the language. This verification process can be represented 
-using a binary relation $R$ between the set of statements (S) and the 
-set of witnesses ($W$), where $(s, w) \in R$ if the witness $w$ 
-demonstrates that the statement $s$ is in the language.
+\section{Introduction}
 
-Sigma protocols are a class of cryptographic protocols that are used to prove the 
-knowledge of a witness for a given statement.
+\textbf{Emphasise how Sigma protocol is still used in elections to a public office}
+Despite the recent growth and popularity of zero-knowledge succinct 
+argument of knowledge (ZKSNARK), sigma protocol remains a
+leading cryptographic proof system in privacy-preserving voting systems. 
+Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
+Belenois --used in French elections for overseas 
+voters\footnote{VVFE, used in French elections, is a derivative of (part of) Belenios and 
+inherited all the zero-knowledge proofs from Belenois.}-- \cite{cortier2023french}, and 
+SwissPost --used in Swiss elections for overseas voters-- voting 
+systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
+Moreover, recently zero-knowledge proof community started a movement to standardise
+the sigma protocol \cite{ZKProof}.
+One of the main reasons for its popularity in privacy-preserving voting systems is its simplicity and 
+well-understood security.
 
-They are used in various cryptographic 
-applications such as identification, authentication, and zero-knowledge proofs. 
-The security of these protocols is based on the hardness of certain mathematical 
-problems such as the discrete logarithm problem. Amongst sigma protocols, 
-one of the most well-known protocols is the Schnorr protocol. In this 
-paper, we present a formal verification of the Schnorr protocol in the
-Coq proof assistant.
+%\textbf{Introduce here that sigma protocol is efficient and simple and all other details about sigma protocol.} 
+Zero-knowledge proofs are possible for all problems in the $NP$ complexity class, which 
+includes problems where a proof of membership can be efficiently verified in polynomial time.
+Sigma protocol is a simple and efficient zero-knowledge proof where the verifier  is assumed to be honest. 
+More formally, for a given $NP$-relation $R$ and a statement $x$, a sigma protocol allows a prover 
+$P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
+that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a three move 
+interactive protocol (shown below). At the end of the protocol $V$ either accepts or rejects the proofs.
+Like any other proof system, sigma protocols also has completness and (special) soundness; moreover,  
+it also has an additional property (special honest-verifier) zero-knowledgeness.
 
-\section{Sigma Protocols}
+\textbf{Draw a move }
 
-  Explain here the definition of Sigma Protocols and the Schnorr protocol.
+\definition{Completeness}
+when $P$ and $V$ follow the protocol, then $V$ always accepts. In other words, 
+if $P$ knows $w$ for $x$ then it would successfully construct a triple 
+(a; c; r) that always passes the verification equation, i.e., $V$ accepts.
+
+\definition{Special soundness}
+there exists a probabilistic polynomial time extractor $E$ which given 
+two accepting transcripts (a; c; r) and (a; c', r') for $x$, then 
+it can extract a witness $w$ such that $(x, w) \in R$. In other words, 
+if $P$ does not know $w$ for $x$ then it cannot create a proof 
+(a; c; r) that will passes the verification check.
+
+\definition{Special honest-verifier zero-knowledge proof}
+there exists a probabilistic polynomial-time simulator S that for  
+any $v$ in $L_R$ and $c \in C$, $S$ generates conversations 
+(a,c,r) with the same probability as honest conversations between 
+$P$ and $V$ using $w$ satisfying $(v,w) \in R$.
+
+Sigma protocol was first defined by Ronald Cramer \cite{cramer1996modular} 
+and the first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
+Eventhough there exists many sigma protocols, the Schnorr protocol is one of the most well-known
+sigma protocol and is used extensively in privacy-preserving voting systems, e.g, Helios, 
+Belenois, SwissPost, etc. Therefore, our formalisation is geared towards the Schnorr protocol; moreover, we 
+also formalise $n$ PARALLEL composition, $n$ AND composition, $n$ OR composition, 
+and $n$ EQ composition of Schnorr protocol. We also formalise Okamoto protocol as a subprotocol 
+for NEQ composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
+much use of Okamoto protocol in the privacy-preserving voting systems, 
+at least in the existing voting systems. Ideally, given the abstraction of 
+our formlisation (vector space) we could have abstracted the 
+sigma protocol and their composition in a generic way \cite{10.1007/978-3-642-02384-2_17},
+but we decided to focus on the Schnorr protocol and its composition to ensure nice and familiar APIs 
+for e-voting in Web Assembly and Rust.
+
+There are numerous implementations of sigma protocol in various languages, 
+e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
+However, there are two main issues with these implementations: (i)  
+the same code is written twice 
+once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java),
+especially in privacy-preserving voting systems such as Helios, SwissPost, and 
+(ii) none of these implementations offer any formal guarantees about the correctness of the code.
+Given the importance of sigma protocols in privacy-preserving voting systems,
+it has been formalised before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
+\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
+pen-and-paper proofs of sigma protocol into theorem provers and not extracting an executable code.
+On the other hand, \cite{10.1145/3319535.3354247} exatract an OCaml code from Coq 
+formalisation but it is mostly geared towards verifying an Helios election transcript, 
+rather than constructing the primitives to conduct an election. Moreover, 
+it lacks many primitives and does not reason about probabilities in an intuitive way.
+
+\subsection{Contribution}
+In this paper, we present a certified implementation sigma protocol and its composition 
+in the Coq proof assistant.
+
+Moreover, we extract WebAssembly and Rust code from our 
+certified implementation. 
+We use our formalisation to model the cryptographic protocols implemented in Helios, 
+Belenois, and SwissPost voting systems. To the best of our knowledge, this is the first
+formal verification of Sigma protocol that can be used at the front-end (WebAssembly code) and
+back-end (Rust code).
+
+\section{Coq formalisation}
+
+  We briefly explain the Schnorr protocol, which is very similar to 
+  the one we explained in the introduction section.
+  Given some public input $(G, g, q, h)$ where $G$
+  is a cyclic group of prime order $q$, and $g$ and $h$ are two 
+  generators of the group $G$, the prover claims that they know a
+  witness $w$ for the statement $h = g^w$; the existence of such
+  a $w$ is immediate because $g$ generates the group. However,
+  does the prover know the witness $w$? In order to convince the
+  verifier, the prover and the verifier do the following:
+  \begin{itemize}
+    \item the prover picks a random number $u$, computes $c = g^u$,
+    and sends $c$ to the verifier.
+    \item the verifier picks a random challenge $e$ and sends it to
+    the prover
+    \item the prover computes $t = u + e * w$ and sends $t$ to the
+    verifier
+  \end{itemize}
+
+The verifier accepts if $g^t = c * h^e$, otherwise rejects. 
+We model the Schnorr protocol in Coq as follows:
+
+\begin{lstlisting}[language=Coq]
+  Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
+    @sigma_proto 1 1 1 :=  ([g^u]; [c]; [u + c * x]).
+\end{lstlisting}
+
+ where $F$ is the underlying field, $G$ is the underlying group,
+ $+ : F \rightarrow F \rightarrow F$ is field addition,
+ $* : F \rightarrow F \rightarrow F$ is field multiplication, and
+ $\textasciicircum : G \rightarrow F \rightarrow G$ scalor multiplication. 
+ We emphasise that we work in abstract setting of \textbf{vector space} to 
+ make the implementation as general as possible. Recall that a vector space consists of a set of 
+ vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
+ two operations: vector addition and scalar multiplication.
+
+\begin{itemize}
+    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
+    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
+\end{itemize}
+
+These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
+(i) \textbf{Closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{Commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
+(iii)  \textbf{Associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
+(iv) \textbf{Existence of zero vector:} There exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
+(v) \textbf{Existence of additive inverse:} For each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
+(vi) \textbf{Closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
+(vii) \textbf{Distributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
+and (viii) \textbf{Compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
+In our setting we instantiate the set of vectors with group $G$ and field with $F$. Moreover, our notation for scalar multiplication 
+is $\textasciicircum$ because it represents, when instantiated concretely, exponentiation function. Finally, 
+we define two more functions
+
+\begin{lstlisting}[language=Coq]
+(* Fake transcript (without the witness x) *)
+Definition schnorr_simulator (g h : G) (u c : F) : 
+@sigma_proto 1 1 1 := ([gop (g^u) (h^(opp c))]; [c]; [u]).
+
+(* 
+  This function checks if a conversation (a; c; r) 
+  is accepting or not. It checks if g^r = a * h^c
+*)
+Definition accepting_conversation 
+  (g h : G) (v : @sigma_proto 1 1 1) : bool :=
+  match v with
+  | (a; c; r) =>  
+    match Gdec (g^(hd r)) (gop (hd a) (h^(hd c))) with 
+    | left _ => true
+    | right _ => false 
+    end
+  end.
+
+(* Distribution that involves the secret x *)
+Definition schnorr_distribution  (lf : list F) 
+  (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
+  dist sigma_proto :=
+  (* draw u from a random distribution *)
+  u <- (uniform_with_replacement lf Hlfn) ;;
+  Ret (schnorr_protocol x g u c).
+
+(* without secret x *)
+Definition simulator_distribution (lf : list F) 
+  (Hlfn : lf <> List.nil) (g h : G) (c : F) : 
+  dist sigma_proto :=
+  (* draw u from a random distribution *)
+  u <- (uniform_with_replacement lf Hlfn) ;;
+  Ret (schnorr_simulator g h u c).
+\end{lstlisting}
+
+Finally we establish the completeness, special soundness, 
+and special honest-verifier zero-knowledge proof. 
+\begin{lstlisting}[language=Coq]
+Lemma schnorr_completeness : 
+  forall (r c : F) (a : t G 1) (c r : t F 1),
+  (a; c; r) = (schnorr_protocol x g r c) ->
+  accepting_conversation g h (a; c; r) = true.
+Proof. (* proof terms omitted *) Qed.
+
+Lemma simulator_completeness : 
+    forall (r c : F) (a : t G 1) (c r : t F 1),
+    (a; c; r) = (schnorr_simulator g h r c) ->
+    accepting_conversation g h (a; c; r) = true.
+  Proof using -(x R). (* proof terms omitted *) Qed.
+
+Lemma special_soundness: 
+  forall (a : G) (ca ra cb rb : F), ca <> cb ->
+  accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
+  accepting_conversation g h ([a]; [cb]; [rb]) = true ->
+  (* then we can find a witness y such that g^y = h *)
+  exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
+Proof using -(x R). (* proof terms omitted *) Qed.
+
+(* it's identical, i.e., information theoretic zero-knowledge proof *)
+(* Under the hood, it is modelled as a list and looks like:
+    [((a; c; r), prob); ((a; c; r), prob) ......].
+  We map accepting_conversation to crunch the first pair, 
+  (a, c, r), and produce boolean a value (true), 
+  and then we show that these two distribution are 
+  identical 
+*)
+Lemma special_honest_verifier_zkp : 
+  forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
+  List.map (fun '(a, p) => (accepting_conversation g h a, p))
+    (@schnorr_distribution lf Hlfn x g c) = 
+  List.map (fun '(a, p) => (accepting_conversation g h a, p))
+    (@simulator_distribution lf Hlfn g h c).
+Proof. (* proof terms omitted *) Qed.
+
+\end{lstlisting}
+
+In our library, we have encoded Parallel composition, 
+AND composition, OR composition, EQ composition, and 
+NEQ composition. Below we explain the OR composition
+beause it is more involved than the rest.
+
+  However, we would like 
+  to emphasise that we worked in a vector-space, rather 
+  than concrete numbers. Working in (abstract) vector-space makes our system 
+  amenable to be instantiated by any group and field 
+  (Elliptic curve vs Concrete Nubmers). \textbf{Currently, 
+  our library comes with concrete nubmers but it can easily be 
+  instantiated with Elliptic curve cryptography}
+
+  \textbf{Coq code of Schnorr goes here}
+
+  The reader can see that we have used vector space. Now 
+  we establish completeness, (special) soundness, and zero-knowledge 
+  proof of knowledge (ZkPOK).
+
+  \textbf{Coq code soundness, completeness, zkp goes here}
+
+  The proof of completeness and soundness are fairly straightforward but 
+  zero-knowledge proof of knowledge requires probabilistic reasoning.
+
+  \textbf{Coq code goes here}
+
+  In our library, we have encoded Parallel composition, 
+  And composition, Or composition, EQ composition, and 
+  NEQ composition. Below we explain the OR composition
+  beause it is more involved than the rest.
+
+  \textbf{OR composition and Coq code}
 
@@
 
-\section{Formal Verification of Sigma Protocols}
+  \subsection{Uniform Distribution}
+  To reason about probabilistic distribution, 
+  we have encoded probability as list.
+
+  \subsection{Fiat-Shamir Transform}
+ We have formalised the interactive version of sigma protocol. However,
+ interaction is not convenient and therefore
+ we use Fiat-Shamir transform to make it non-interactive. We use SHA256 
+ to turn the interaction to non-interaction but in order to 
+ make it a self-contained library and 
+ avoid relying on any external library at the front-end (WebAssembly)
+ we have encoded the SHA256 in the Coq theorem prover, with usual correctness 
+ properties.
+
+ \subsection{Efficient Modular Arithmetic}
+  In order to call the functions from our formalisation, 
+  a user need to instantiate
 
@@
 
-\section{Case Studies}
+\section{Case Studies/Experiment}
   We use our formalisation to model the Cryptographic protocols implemented in 
-  Helios voting systems.
+  Helios voting systems. Compare it with state-of-the-art 
+  crypto library.
 
@@
 \section{Conclusion, Future Work, and Limitations}
+  In this paper, we present a certified implementation 
+  that can be readily used by voting community and 
+  we demonstrated the usefulness by encoding Helios, 
+  Belenois, and SwissPost using our primitives. 
+  Moreover, our formalisation extracts to WebAssembly and 
+  Rust without duplicate efforts.
+
+\section{DECRA}
+The aim of this project is to investigate the applicability of 
+zero-knowledge succinct argument of knowledge (ZKSNARK) 
+to reduce the data breaches.
 

### 2024-05-22 paper/CCS/paper.tex
Paper draft

--- 2024-05-09 paper/paper.tex
@@
   and verifiability of elections and still used in prominent e-voting systems such as 
-  Helios, Belenois, and SwissPost \textbf{More examples}. However, 
+  Helios, Belenois, and SwissPost. However, 
   the existing implementations of sigma protocol have two 
@@
 \section{Introduction}
+
+Electronic voting offers convenience and efficiency in an electoral process, 
+potentially improving accessibility for disabled voters, increasing participation 
+among overseas voters, and lowering the costs associated with conducting elections.
+To ensure that electronic voting adheres to the principles of a (free and fair) 
+paper-ballot election, we need two important ingredients: privacy and 
+verifiability. We achieve privacy in a paper-ballot election by ensuring 
+that no identifying present on a ballot to the voter, and verifiability 
+is ensured by means of scrutineers. To have a similar effect in electronic 
+voting, robust encryption techniques is employed to safeguard the privacy 
+of voter choices, while audit trails (zero-knowledge proof)
+allow voters and independent observers to verify the integrity 
+of the voting process. But even the most 
+sophisticated cryptographic techniques are useless if their software
+implementation contains bugs. In fact, 
+there is a history of bugs, varying from trivial to critical, 
+in electronic voting software programs employed for democratic 
+elections, e.g., Scytl/SwissPost \cite{9152765} (used in Swiss election), 
+Voatz \cite{255334} (used in West Virginia, USA election),
+Democracy Live Online Voting System \cite{263858} 
+(used in Delaware, West Virginia, and New Jersey, USA election), 
+Moscow Internet Voting System \cite{10.1007/978-3-030-51280-4_3}
+(used in Russia election), iVote System \cite{10.1007/978-3-319-22270-7_3, 10.1145/3014812.3014837} 
+(used in New South Wales, Australia election). 
+Most of these software programs 
+establish their correctness by means of testing, which 
+does not capture all the possible scenarios. 
+Interestingly, most of these bugs were found by researchers
+who inspected the code after the source code was made public, 
+even though the companies developing these proprietary software programs had 
+claimed that they were bug free.
+
+Two imporant ingredients for 
+electronic voting are privacy and verifiability. While privacy 
+ensures that no ... while verifiability ensures ....
+
+Cryptographic techniques are used to achive privacy 
+but even the most 
+sophisticated cryptographic techniques are useless if their software
+implementation contains bugs.
+
+However, security 
+experts often find the vulnerabilities in the deployed software that 
+could undermine the integrity of an election (\textbf{cite all the work of 
+software bug}).
+
+Despite the concerns, many jurisdictions are already using 
+electronic voting as a means to modernising their electoral process.
+
+But even the most 
+sophisticated cryptographic techniques are useless if their software
+implementation contains bugs, and so evoting also requires
+“software independence”
 
@@
 and special honest-verifier zero-knowledge proof.
+
 \begin{lstlisting}[language=Coq]
@@
 
+\begin{lstlisting}[language=Coq]
+
+\end{lstlisting}
+
   However, we would like 
@@
 
-  \subsection{Parallel Composition}
-  Explain the parallel composition of sigma protocols.
-
-  \subsection{And Composition}
-  Explain the and composition of sigma protocols.
-
-  \subsection{Or Composition}
-  Explain the or composition of sigma protocols.
-
-  \subsection{Equality Composition}
-  Explain the equality composition of sigma protocols.
-
-  \subsection{Inequality Composition}
-  Explain the inequality composition of sigma protocols.
-
   \subsection{Uniform Distribution}
@@
   we have encoded probability as list.
+
+  \subsection{Efficient Modular Arithmetic}
+  In order to call the functions from our formalisation, 
+  a user need to instantiate
 
@@
  properties.
-
- \subsection{Efficient Modular Arithmetic}
-  In order to call the functions from our formalisation, 
-  a user need to instantiate
 
@@
 
-\section{DECRA}
-The aim of this project is to investigate the applicability of 
-zero-knowledge succinct argument of knowledge (ZKSNARK) 
-to reduce the data breaches.
-
 %%

### 2024-05-22 paper/IEEES/paper.tex
Paper draft

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

\usepackage{listings}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{url}
\usepackage{lstcoq}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Hope}

\author{Anonymous}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  Despite the recent growth of zero-knowledge succinct argument 
  of knowledge (ZkSNARK) in cryptocurrencies, 
  sigma protocol remains a popular choice in electronic voting to maintain privacy 
  and verifiability of elections and still used in prominent e-voting systems such as 
  Helios, Belenois, SwissPost, etc. However, 
  the existing implementations of sigma protocol have two 
  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
  and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
  and (ii) none of these implementations offer any security guarantees. 
  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant and
  prove our implementation is (special) sound, complete, and 
  (honest verifier) zero-knowledge. Finally, 
  we compile our Coq formalisation to WebAssembly and Rust, and 
  thereby solve the problem of writing the same code twice. 
  We demonstrate the applicability of our
  formalisation by encoding the sigma protcol implemented in 
  Helios, Belenois, and SwissPost voting systems. 
  Our long terms goal is to provide a verified cryptographic library that can be 
  readily used in privacy-preserving voting systems.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\iffalse
\section{How to pitch this paper and What is the unique selling point of our work?}
Our Coq formalisation can be used at front-end (WebAssembly code) and 
back-end (Rust). Contrary to the existing work, our formalisation
does not write the same code twice. But sigma protocol is arcane and has 
been formalised couple of times before so why another formalisation?
None of the formalisation has been able to extract the code to executable code 
and one that was able to do so did not reason about probabilities in an intuitive way.
Moreover, that work was just geared towards verifying a transcript rather than
constructing it. Also, recently ZKP community started a movement to 
formalise the sigma protocols. We also demonstrates the 
applicability of our formalisation by encoding Helios cryptographic protocols
in our formalisation.

\textbf{We need to explain why formal verification is important in the context of voting systems.}

\begin{itemize}
  \item Explain zero-knowledge proofs (completeness, soundness, zero-knowledge)
  \item Explain sigma protocols (completeness, special-soundness, honest-verifier zero-knowledg) 
  and mention about the Schnorr protocol
  \item Our contribution
  \item Explain the Schnorr protocol
  \item Explain Parallel, And, Eq, Or, and NEQ relations (also explain that 
  most of the formalisation has worked on And and Or relations)
\end{itemize}

\fi

\section{Introduction}
Electronic voting offers convenience and efficiency in electoral processes, 
potentially improving accessibility for disabled voters, increasing participation 
among overseas voters, and lowering the costs associated with conducting elections.
Privacy and verifiability are two crucial elements that a voting system 
must ensure to adhere with the principles of a free-and-fair election.  
In a paper-ballot election, we achieve privacy by ensuring that 
no identifying information is present on a ballot that links the ballot to a particular voter
and verifiability by means of scrutineers closely observing various electoral 
processes, including counting of ballots. In order to have a similar effect in electronic 
voting, encryption is employed to safeguard the privacy 
of voter choices, while public verifiable evidences (zero-knowledge proof)
allow voters and independent observers to verify the integrity 
of the voting process. However, a cryptographic techniques, no matter how 
advance,  are useless if their software implementation contains bugs. 
In fact, due to a major cryptographic flaw that
could let someone change votes cast using Switzerland's online 
voting software without being detected  \cite{9152765}, the Swiss Federal Chancellery suspended electronic voting in 
2019. It only resumed in 2023 after getting feedbacks from academic 
community \cite{swiss_evoting_chronik} about various component used in 
the electronic voting software. However, it is not an isolated  
instance where bugs have been found in a voting software, e.g., 
Voatz \cite{255334} (used in West Virginia, USA election),
Democracy Live Online Voting System \cite{263858} 
(used in Delaware, West Virginia, and New Jersey, USA election), 
Moscow Internet Voting System \cite{10.1007/978-3-030-51280-4_3}
(used in Russia election), and iVote System \cite{10.1007/978-3-319-22270-7_3, 10.1145/3014812.3014837} 
(used in New South Wales, Australia election), etc. 
These unfortunate situations can largely be attributed to two factors: 
(i) closed source code (proprietary artifacts) because most of these bugs were 
discovered by researchers who inspected the code after they were made public, and 
(ii) software testing which is inadequate to rule out all the bugs 
from a software. To eliminate potential bugs from software, formal verification has 
emerged as a promising solution. In recent years, it has been increasingly 
adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
including cryptography \cite{8835346,10.1145/3133956.3134043,190894,10.1145/2701415,
10.1145/2660267.2660370,10.1145/3319535.3363211}.

\textbf{Our contributions:}
In this paper, we present a certified implementation of the Sigma protocol --an efficient 
type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
the Coq proof assistant. We have formalised and analysed the interactive version of 
the Sigma protocol, but in practice it is not convenient due to the required interaction. 
Therefore, all Sigma protocol implementations use the Fiat-Shamir 
transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
using a hash function to replace the randomness of the public-coin verifier, though 
some care is required \cite{10.1007/978-3-642-34961-4_38}.
To make our formalisation self-contained and independent of external libraries, we have 
encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
have implemented efficient prime field arithmetic procedures and the Schnorr group to 
ensure our library is concrete and executable. Finally, we extract WebAssembly and 
Rust code from our certified implementation, one of the novelties of our 
formalisation.

There are numerous implementations of sigma protocol in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: 
(i) the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java) and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Therefore, we use our formalisation to model the sigma protocol implemented in Helios, 
Belenois, and SwissPost voting systems to demonstrate the usablity of 
our library. Unlike Helios and SwissPost,
we write one implementation and extract WebAssembly (front-end) and Rust (back-end). 
Belenois is slightly different in this respect and uses Js\_of\_ocaml 
to compile the OCaml code into JavaScript so it has only one 
implementation written in OCaml; nonetheless it is not verified 
and offers no formal guarantees. To the best of our knowledge, 
this is the firstformal verification of sigma protocol that can be used at 
the front-end (WebAssembly code) and back-end (Rust code).

\subsection{Outline}

\section{Sigma Protocol}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), sigma protocol remains a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
Belenois --used in French elections for overseas 
voters\footnote{VVFE, used in French elections, is a derivative of (part of) Belenios and 
inherited all the zero-knowledge proofs from Belenois.}-- \cite{cortier2023french}, and 
SwissPost --used in Swiss elections for overseas voters-- voting 
systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
Moreover, recently zero-knowledge proof community started a movement to standardise
the sigma protocol \cite{ZKProof}.
One of the main reasons for its popularity in privacy-preserving voting systems is its
well-understood security.  Other application of sigma protocol 
include identification schemes, (cite more work).

%\textbf{Introduce here that sigma protocol is efficient and simple and all other details about sigma protocol.} 
Zero-knowledge proofs were first studied by Goldwasser, Micali, and Rackoff \cite{10.1145/22145.22178} and 
are possible for all problems in $NP$ \cite{10.1145/116825.116852}. Recall that $NP$ is the class of 
problems that have efficient verifiers; that is, for a given problem in the $NP$ class, there is 
a polynomial-time algorithm that can verify whether a given solution, or witness, to the problem is correct or not.
More formally, for a given $NP$-relation $R$ and a statement $x$, zero-knowledge proof allows a prover 
$P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a 
interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
\textit{Sigma protocol}, \textbf{shown in the figure }, is an efficient three move zero-knowledge proof where the 
verifier is assumed to be honest and characterised by completeness, (special) soundness, and 
(special honest-verifier) zero-knowledge. More formally: 
\begin{itemize}
  \item \textbf{Completeness:}
  when $P$ and $V$ follow the protocol, $V$ always accepts. 
  In other words, if $P$ knows $w$ for $x$ such that ($x$, $w$) $\in$ $R$,  
  then $P$ can successfully construct a proof $(a, c, r)$ that always passes the verification equation, 
  i.e., $V$ accepts.

\item \textbf{Special soundness:}
there exists a polynomial-time extractor $E$ which given 
two accepting transcripts $(a, c, r)$ and $(a, c', r')$ for $x$, 
it can extract a witness $w$ such that $(x, w) \in R$. In other words, 
if $P$ does not know $w$ for $x$ then it cannot construct a proof 
(a; c; r) that will passes the verification check. 
\item \textbf{Special honest-verifier zero-knowledge proof:}
There exists a polynomial-time simulator $S$ that, for any 
$v \in L_R$ where $L_R = \{x  \mid (x, w) \in R\}$,
generates an accepting transcript $(a, c, r)$ 
without using the witness $w$. 
This transcript is indistinguishable from one produced by an 
honest conversation between $P$ and $V$ using $w$, 
satisfying $(v,w) \in R$.

\end{itemize}

\textbf{Draw a picture here of sigma protocol}

Sigma protocol was first defined by Ronald Cramer \cite{cramer1996modular} 
and the first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
Eventhough there exists many sigma protocols, the Schnorr protocol is used extensively in privacy-preserving voting systems, e.g, Helios, Belenois, SwissPost, etc. Therefore, 
our formalisation is geared towards the Schnorr protocol. 
Moreover, we also formalise the composition of (i) $n$ \textit{Parallel} Schnorr, 
(i) $n$ \textit{And} Schnorr, (iii) $n$ \textit{Or} Schnorr, and (iv) $n$ \textit{Eq} Schnorr protocol. 
Ideally, given the abstraction of our formlisation (\textit{vector space}), we could have 
abstracted the sigma protocol and their composition in a generic way \cite{10.1007/978-3-642-02384-2_17},
but we decided to focus on the Schnorr protocol and its composition to ensure familiar APIs 
for e-voting in WebAssembly and Rust. We also formalise Okamoto protocol as a subprotocol 
for Neq composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
much use of Neq in the privacy-preserving voting systems, at least in the existing voting systems.

\section{Coq formalisation}

  We briefly explain the Schnorr protocol, which is very similar to figure \textbf{refer here to sigma protocol picture}.
  Given some public input $(G, g, q, h)$ where $G$
  is a cyclic group of prime order $q$, $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $c = g^u$,
    and sends $c$ to the verifier.
    \item the verifier picks a random challenge $e$ and sends it to
    the prover
    \item the prover computes $t = u + e * w$ and sends $t$ to the
    verifier
  \end{itemize}

The verifier accepts if $g^t = c * h^e$, otherwise rejects. We can prove that 
this protocol has completeness, special soundness, and special honest-verifier 
zero-knowledge proof.

\begin{itemize}
  \item completeness: when $P$ and $V$ both follows the protocol, $V$ accepts the proof, i.e., 
  the verification equation checks. We can see by algebraic simplification that is the case.
    \begin{align*}
      g^t = g^{u + e * w} = g^u * (g^w)^e = c * h^e
    \end{align*}
  \item special soundness:

  \item special honest-verifier zero-knowledge proof:

\end{itemize}

In the Schnorr protocol, $g, h, c$ are group elements from underlying group, while 
$u, e, t$ are scalar values from underlying prime field. In practice, 
both the group elements and the fields elements are some large prime numbers,
albeit the operations differ. For most of the languages it does not matter, 
but also a potential source of bugs (cite thomas work here). However, 
we need to flesh down all the details while encoding it Coq. One possibility is 
to encode the Coq functions to work with concrete numbers but this leads to 
cumbersome proofs because of dealing with concrete numbers. In our formalisation, 
we decided to abstract the underlying group as an abstract type $G$, endowed with 
usual group operation, and the underlying field as an abstract type $F$, endowed with 
filed operation. Finally, we abstract these two types in an vector space. This 
makes our formalisation generic that can be instantiated with 
any kind of group and field as long as it follows the axioms of 
vector space. For example, in our formalisation we have developed 
efficient algorithm for Schnorr group but our formalisation can 
later be also instantiated with elliptic curve group. However, 
one of the major benefit of this abstraction is easiness of proofs 
which can be easily automated.

We model the Schnorr protocol in Coq as follows:

\begin{lstlisting}[language=Coq]
  Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
    @sigma_proto 1 1 1 :=  ([g^u]; [c]; [u + c * x]).
\end{lstlisting}

 where $F$ is the underlying field, $G$ is the underlying group,
 $+ : F \rightarrow F \rightarrow F$ is field addition,
 $* : F \rightarrow F \rightarrow F$ is field multiplication, and
 $: G \rightarrow F \rightarrow G$ scalor multiplication. 
 We emphasise that we work in abstract setting of \textbf{vector space} to 
 make the implementation as general as possible. Recall that a vector space consists of a set of 
 vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
 two operations: vector addition and scalar multiplication.

\begin{itemize}
    \item \textit{Vector addition}: for any vectors \(\mathbf{v}, \mathbf{w} \in V\), their sum, denoted by \(\mathbf{v} + \mathbf{w}\), is also in \(V\).
    \item \textit{Scalar multiplication}: for any vector \(\mathbf{v} \in V\) and any scalar \(c \in F\), their product, denoted by \(c\mathbf{v}\), is also in \(V\).
\end{itemize}

These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
(i) \textbf{Closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{Commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
(iii)  \textbf{Associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
(iv) \textbf{Existence of zero vector:} There exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
(v) \textbf{Existence of additive inverse:} For each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
(vi) \textbf{Closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
(vii) \textbf{Distributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
and (viii) \textbf{Compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
In our setting we instantiate the set of vectors with group $G$ and field with $F$. Moreover, our notation for scalar multiplication 
is because it represents, when instantiated concretely, exponentiation function. Finally, 
we define two more functions

\begin{lstlisting}[language=Coq]
  (* Fake transcript (without the witness x) *)
  Definition schnorr_simulator (g h : G) (u c : F) : 
  @sigma_proto 1 1 1 := ([gop (g^u) (h^(opp c))]; [c]; [u]).

  (* 
    This function checks if a conversation (a; c; r) 
    is accepting or not. It checks if g^r = a * h^c
  *)
  Definition accepting_conversation 
    (g h : G) (v : @sigma_proto 1 1 1) : bool :=
    match v with
    | (a; c; r) =>  
      match Gdec (g^(hd r)) (gop (hd a) (h^(hd c))) with 
      | left _ => true
      | right _ => false 
      end
    end.

  (* Distribution that involves the secret x *)
  Definition schnorr_distribution  (lf : list F) 
    (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
    dist sigma_proto :=
    (* draw u from a random distribution *)
    u <- (uniform_with_replacement lf Hlfn) ;;
    Ret (schnorr_protocol x g u c).

  (* without secret x *)
  Definition simulator_distribution (lf : list F) 
    (Hlfn : lf <> List.nil) (g h : G) (c : F) : 
    dist sigma_proto :=
    (* draw u from a random distribution *)
    u <- (uniform_with_replacement lf Hlfn) ;;
    Ret (schnorr_simulator g h u c).
  \end{lstlisting}

  Finally we establish the completeness, special soundness, 
  and special honest-verifier zero-knowledge proof.

  \begin{lstlisting}[language=Coq]
  Lemma schnorr_completeness : 
    forall (r c : F) (a : t G 1) (c r : t F 1),
    (a; c; r) = (schnorr_protocol x g r c) ->
    accepting_conversation g h (a; c; r) = true.
  Proof. (* proof terms omitted *) Qed.

  Lemma simulator_completeness : 
      forall (r c : F) (a : t G 1) (c r : t F 1),
      (a; c; r) = (schnorr_simulator g h r c) ->
      accepting_conversation g h (a; c; r) = true.
    Proof using -(x R). (* proof terms omitted *) Qed.

  Lemma special_soundness: 
    forall (a : G) (ca ra cb rb : F), ca <> cb ->
    accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
    accepting_conversation g h ([a]; [cb]; [rb]) = true ->
    (* then we can find a witness y such that g^y = h *)
    exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
  Proof using -(x R). (* proof terms omitted *) Qed.

  (* it's identical, i.e., information theoretic zero-knowledge proof *)
  (* Under the hood, it is modelled as a list and looks like:
      [((a; c; r), prob); ((a; c; r), prob) ......].
    We map accepting_conversation to crunch the first pair, 
    (a, c, r), and produce boolean a value (true), 
    and then we show that these two distribution are 
    identical 
  *)
  Lemma special_honest_verifier_zkp : 
    forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
    List.map (fun '(a, p) => (accepting_conversation g h a, p))
      (@schnorr_distribution lf Hlfn x g c) = 
    List.map (fun '(a, p) => (accepting_conversation g h a, p))
      (@simulator_distribution lf Hlfn g h c).
  Proof. (* proof terms omitted *) Qed.

  \end{lstlisting}

In our library, we have encoded Parallel composition, 
AND composition, OR composition, EQ composition, and 
NEQ composition. Below we explain the OR composition
beause it is more involved than the rest.

  However, we would like 
  to emphasise that we worked in a vector-space, rather 
  than concrete numbers. Working in (abstract) vector-space makes our system 
  amenable to be instantiated by any group and field 
  (Elliptic curve vs Concrete Nubmers). \textbf{Currently, 
  our library comes with concrete nubmers but it can easily be 
  instantiated with Elliptic curve cryptography}

  \textbf{Coq code of Schnorr goes here}

  The reader can see that we have used vector space. Now 
  we establish completeness, (special) soundness, and zero-knowledge 
  proof of knowledge (ZkPOK).

  \textbf{Coq code soundness, completeness, zkp goes here}

  The proof of completeness and soundness are fairly straightforward but 
  zero-knowledge proof of knowledge requires probabilistic reasoning.

  \textbf{Coq code goes here}

  In our library, we have encoded Parallel composition, 
  And composition, Or composition, EQ composition, and 
  NEQ composition. Below we explain the OR composition
  beause it is more involved than the rest.

  \textbf{OR composition and Coq code}

  \subsection{Uniform Distribution}
  To reason about special honest-verifier zero-knowledge proof 
  intuitively, we need a model of uniform distribution. 
  we encode distribution a list of tuples where the 
  second element of tuple basically is probability of first element 
  in the tuple. Moreover, we define equality on distribution by 
  stating that two distributions are equal if they are permutation 
  of each other.

  \begin{lstlisting}[language=Coq]

  (* Probability Distribution on a type A *)
  Definition dist (A : Type) : Type := list (A * prob).

  Definition dist_equiv {A : Type} : relation (dist A) := 
  fun xs ys => Permutation xs ys.

  (* Probability Monad *)
  Definition Ret {A : Type} (x : A) : dist A := [(x, one)].

  Fixpoint Bind {A B : Type} (xs : dist A)  
    (f : A -> dist B) : dist B := 
    match xs with 
    | [] => [] 
    | (ax, px) :: tx => 
      List.append (List.map (fun '(ut, pt) => 
      (ut, mul_prob px pt)) (f ax)) (Bind tx f)
    end.

    (* Uniform distribution u*)
    Definition uniform_with_replacement {A : Type} : 
      forall (l : list A), l <> [] -> dist A.
    Proof.
      intros ? H.
      remember (Pos.of_nat (List.length l)) as len.
      exact (List.map 
        (fun x => (x, mk_prob 1 len)) l).
    Defined.

    Fixpoint repeat_dist_ntimes_vector {A : Type} 
      (d : dist A) 
      (n : nat) : dist (Vector.t A n) := 
    match n with 
    | 0 => Ret (@Vector.nil A)
    | S n' => 
      Bind d (fun u => 
        Bind (repeat_dist_ntimes_vector d n')
        (fun v => Ret (Vector.cons _ u _ v)))
    end.

    Lemma uniform_probability_multidraw_prob {A : Type} :
      forall n lf (a : Vector.t A n) b (Hlf : lf <> []), 
      In (a, b) (repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlf) n) ->
      b = mk_prob 1 (Pos.of_nat 
      (Nat.pow (List.length lf) n)).
  \end{lstlisting}

  We use the $uniform\_probability\_multidraw\_prop$ theorem 
  for special honest-verifier zero-knowledge proof.

  \begin{lstlisting}[language=Coq]

(* schnorr distribution *)
    Definition generalised_or_schnorr_distribution  
      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
      (x : F) (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
      dist (@sigma_proto (m + (1 + n)) 
        (1 + (m + (1 + n))) (m + (1 + n))) :=
      (* draw ((m + (1 + n)) + (m + n)) random elements *)
      usrs <- repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
      Ret (construct_or_conversations_schnorr x gs hs usrs c).

    (* simulator distribution *)
    Definition generalised_or_simulator_distribution  
      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
      (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
      dist (@sigma_proto (m + (1 + n)) 
        (1 + (m + (1 + n))) (m + (1 + n))) :=
      (* draw ((m + (1 + n)) + (m + n)) random elements *)
      usrs <- repeat_dist_ntimes_vector 
        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
      Ret (construct_or_conversations_simulator gs hs usrs c).

  \end{lstlisting}

  \subsection{Efficient Modular Arithmetic}
  In order to call the functions from our formalisation, 
  a user need to instantiate

  \subsection{Fiat-Shamir Transform}
 We have formalised the interactive version of sigma protocol. However,
 interaction is not convenient and therefore
 we use Fiat-Shamir transform to make it non-interactive. We use SHA256 
 to turn the interaction to non-interaction but in order to 
 make it a self-contained library and 
 avoid relying on any external library at the front-end (WebAssembly)
 we have encoded the SHA256 in the Coq theorem prover, with usual correctness 
 properties.

\section{Web Assembly and Rust from the Coq Formalisation}
  Bas Spitter

\section{Case Studies/Experiment}
  We use our formalisation to model the Cryptographic protocols implemented in 
  Helios voting systems. Compare it with state-of-the-art 
  crypto library.

\section{Related Work}
  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.

\textbf{find the shortcomings of these works}
Given the importance of sigma protocols in privacy-preserving voting systems,
it has been formalised before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
pen-and-paper proofs of sigma protocol into theorem provers and not extracting an executable code.
On the other hand, \cite{10.1145/3319535.3354247} extract an OCaml code from the Coq 
formalisation but it is mostly geared towards verifying an Helios election transcript, 
rather than constructing the primitives to conduct an election. Moreover, 
it does not reason about probabilities in an intuitive way.

\section{Conclusion, Future Work, and Limitations}
  In this paper, we present a certified implementation 
  that can be readily used by voting community and 
  we demonstrated the usefulness by encoding Helios, 
  Belenois, and SwissPost using our primitives. 
  Moreover, our formalisation extracts to WebAssembly and 
  Rust without duplicate efforts.

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{IEEEabrv,reference}

% that's all folks
\end{document}

### 2024-05-28 paper/IEEES/paper.tex
Added some more text

@@
   and (ii) none of these implementations offer any security guarantees.
+
   In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant and
   prove our implementation is (special) sound, complete, and 
-  (honest verifier) zero-knowledge. Finally, 
-  we compile our Coq formalisation to WebAssembly and Rust, and 
+  (honest verifier) zero-knowledge. Moreover, 
+  we compile our Coq formalisation to WebAssembly and Rust; 
   thereby solve the problem of writing the same code twice. 
@@
 \section{Introduction}
-Electronic voting offers convenience and efficiency in electoral processes, 
-potentially improving accessibility for disabled voters, increasing participation 
-among overseas voters, and lowering the costs associated with conducting elections.
-Privacy and verifiability are two crucial elements that a voting system 
-must ensure to adhere with the principles of a free-and-fair election.  
-In a paper-ballot election, we achieve privacy by ensuring that 
-no identifying information is present on a ballot that links the ballot to a particular voter
-and verifiability by means of scrutineers closely observing various electoral 
-processes, including counting of ballots. In order to have a similar effect in electronic 
-voting, encryption is employed to safeguard the privacy 
-of voter choices, while public verifiable evidences (zero-knowledge proof)
-allow voters and independent observers to verify the integrity 
-of the voting process. However, a cryptographic techniques, no matter how 
-advance,  are useless if their software implementation contains bugs. 
+Electronic voting offers convenience and efficiency in electoral processes, potentially improving 
+accessibility for disabled voters, increasing participation among overseas voters, and lowering 
+the costs associated with conducting elections. Moreover,
+they can streamline the voting process, reduce administrative burdens, and enable 
+faster tallying of results. However, the transition to electronic voting also brings significant 
+challenges, particularly in ensuring the privacy and verifiability of the voting process. Therefore, 
+privacy and verifiability are two crucial elements that a voting system must ensure to adhere with 
+the principles of a free-and-fair election. In a paper-ballot election, privacy is maintained by 
+ensuring that no identifying information is present on a ballot that links it to a particular voter, 
+and verifiability is achieved through scrutineers closely observing various electoral processes, 
+including the counting of ballots. In order to have a similar effect in electronic voting, encryption 
+is employed to safeguard the privacy of voter choices, while publicly verifiable evidence 
+(such as zero-knowledge proofs) allows voters and independent observers to verify the integrity of 
+the voting process. However, no matter how advanced the cryptographic techniques, they are useless 
+if their software implementation contains bugs.
 In fact, due to a major cryptographic flaw that
@@
 (ii) software testing which is inadequate to rule out all the bugs 
-from a software. To eliminate potential bugs from software, formal verification has 
-emerged as a promising solution. In recent years, it has been increasingly 
+from a software. Therefore, to avoid the situations like this, 
+an electronic voting system must adhere to \textit{software independence}\cite{rivest2008notion}:
+\begin{quote}
+  A voting system is software-independent if an
+  (undetected) change or error in its software cannot
+  cause an undetectable change or error in an
+  election outcome. 
+\end{quote}
+\noindent
+Therefore, many electronic voting systems follow the principals 
+of \textit{end-to-end verifiability}. End-to-end verifiability is 
+defined as: 
+\begin{itemize}
+  \item Cast-as-intended: voters get proof that the electronic ballot accurately reflects their choices.
+  \item Collected-as-cast: the election authority provides proof that the electronic ballots are received without tampering.
+  \item Counted-as-collected: the election authority provides proof that the results are based on correctly counting all received ballots.
+\end{itemize}
+
+\noindent 
+Finally, voters or scrutineers inspect these proofs and accept or reject the election results based on 
+the verification of these proofs. In practice, this means that during the execution of an election, 
+electronic voting software generates data, and voters and scrutineers verify the conformity of 
+this data using independently written computer programs. The rationale is that if there is 
+any discrepancy in the electronic voting system, at least one scrutineer or voter would detect it.
+It is important to note that end-to-end verifiability is a valuable feature because it 
+allows for the verification of the election results by checking the proofs of correctness 
+only after the election has concluded. This ensures that the election process was conducted 
+properly and that the results are accurate, but it is applied after the voting has taken place.
+The question arises: can we use it before an election?
+The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
+it and develop various components of electronic voting 
+software in this formal language. This process is called as formal verification and it ensures 
+that the software always produces valid proofs, 
+which are consistently accepted by voters and scrutineers. In other words, formal verification
+can be employed to develop reliable electronic voting software.
+In fact, formal verification has emerged as a promising solution 
+to eliminate potential bugs from software, and in recent years it has been increasingly 
 adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
@@
 
-\textbf{Our contributions:}
 In this paper, we present a certified implementation of the Sigma protocol --an efficient 
 type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
-the Coq proof assistant. We have formalised and analysed the interactive version of 
+the formal language of Coq proof assistant. Given that the formal language of Coq 
+is constructive, we get an implementation that can be executed on a computer.
+
+We have formalised and analysed the interactive version of 
 the Sigma protocol, but in practice it is not convenient due to the required interaction. 
@@
 one of the major benefit of this abstraction is easiness of proofs 
-which can be easily automated.
-
-We model the Schnorr protocol in Coq as follows:
+which can be easily automated. Therefore, we model the Schnorr 
+protoco, the simulator, and the verification equation in Coq as follows:
 
 \begin{lstlisting}[language=Coq]
+(*Real transcript (involves secret x)*)
 Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
-    @sigma_proto 1 1 1 :=  ([g^u]; [c]; [u + c * x]).
+ sigma_proto :=  ([g^u]; [c]; [u + c * x]).
+
+(*Fake transcript (without the witness x)*)
+Definition schnorr_simulator (g h : G) (u c : F) :
+  sigma_proto := ([gop (g^u) (h^(opp c))]; [c]; [u]).
+
+(*This function checks if a transcript 
+(a; c; r) is accepting or not. It checks
+if g^r = a * h^c*)
+Definition accepting_conversation 
+  (g h : G) (v : sigma_proto) : bool :=
+  match v with
+  | (a; c; r) =>  
+    match Gdec (g^r) (gop a (h^c)) with 
+    | left _ => true
+    | right _ => false 
+    end
+  end.
 \end{lstlisting}
 
+\noindent
  where $F$ is the underlying field, $G$ is the underlying group,
@@
  $* : F \rightarrow F \rightarrow F$ is field multiplication, and
- $: G \rightarrow F \rightarrow G$ scalor multiplication. 
- We emphasise that we work in abstract setting of \textbf{vector space} to 
- make the implementation as general as possible. Recall that a vector space consists of a set of 
+ $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ scalar multiplication of vector space.  
+ Recall that a vector space consists of a set of 
  vectors, denoted by \(V\), a field \(F\) (elements of F are called scalars), and 
  two operations: vector addition and scalar multiplication.
-
 \begin{itemize}
@@
 These operations must satisfy the following properties for all vectors \(\mathbf{u}, \mathbf{v}, \mathbf{w} \in V\) and all scalars \(c, d \in F\):
-(i) \textbf{Closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{Commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
-(iii)  \textbf{Associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
-(iv) \textbf{Existence of zero vector:} There exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
-(v) \textbf{Existence of additive inverse:} For each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
-(vi) \textbf{Closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
-(vii) \textbf{Distributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
-and (viii) \textbf{Compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
-In our setting we instantiate the set of vectors with group $G$ and field with $F$. Moreover, our notation for scalar multiplication 
-is because it represents, when instantiated concretely, exponentiation function. Finally, 
-we define two more functions
+(i) \textbf{closure under addition:} \(\mathbf{u} + \mathbf{v} \in V\), (ii) \textbf{commutativity of addition:} \(\mathbf{u} + \mathbf{v} = \mathbf{v} + \mathbf{u}\), 
+(iii)  \textbf{associativity of addition:} \((\mathbf{u} + \mathbf{v}) + \mathbf{w} = \mathbf{u} + (\mathbf{v} + \mathbf{w})\), 
+(iv) \textbf{existence of zero vector:} there exists a vector \(\mathbf{0} \in V\) such that \(\mathbf{v} + \mathbf{0} = \mathbf{v}\) for all \(\mathbf{v} \in V\), 
+(v) \textbf{existence of additive inverse:} for each vector \(\mathbf{v} \in V\), there exists a vector \(-\mathbf{v} \in V\) such that \(\mathbf{v} + (-\mathbf{v}) = \mathbf{0}\),
+(vi) \textbf{closure under scalar multiplication:} \(c\mathbf{v} \in V\), 
+(vii) \textbf{cistributive properties:} \(c(\mathbf{u} + \mathbf{v}) = c\mathbf{u} + c\mathbf{v}\) and \((c + d)\mathbf{v} = c\mathbf{v} + d\mathbf{v}\), 
+and (viii) \textbf{compatibility with field multiplication:} \(c(d\mathbf{v}) = (cd)\mathbf{v}\) and \(1\mathbf{v} = \mathbf{v}\), where \(1\) denotes the multiplicative identity in \(F\).
+In our setting we instantiate the set of vectors with $G$ and field with $F$. 
+Moreover, our notation for scalar multiplication is $\mbox{\textasciicircum}$ because it represents, 
+when instantiated concretely, exponentiation function but it is purely for notational convenience.
+
+We prove the completeness and special soundness property of the Schnorr protocol, 
+as shown in the figure .... We however cannot prove the special honest-verifier 
+zero-knowledge property yet because it requires reasoning about probability that 
+we discuss in the next section.
 
 \begin{lstlisting}[language=Coq]
-  (* Fake transcript (without the witness x) *)
-  Definition schnorr_simulator (g h : G) (u c : F) : 
-  @sigma_proto 1 1 1 := ([gop (g^u) (h^(opp c))]; [c]; [u]).
+Lemma schnorr_completeness : 
+forall (r c : F) (a : t G 1) (c r : t F 1),
+(a; c; r) = (schnorr_protocol x g r c) ->
+accepting_conversation g h (a; c; r) = true.
+Proof. (* proof terms omitted *) Qed.
 
-  (* 
-    This function checks if a conversation (a; c; r) 
-    is accepting or not. It checks if g^r = a * h^c
-  *)
-  Definition accepting_conversation 
-    (g h : G) (v : @sigma_proto 1 1 1) : bool :=
-    match v with
-    | (a; c; r) =>  
-      match Gdec (g^(hd r)) (gop (hd a) (h^(hd c))) with 
-      | left _ => true
-      | right _ => false 
-      end
+Lemma simulator_completeness : 
+forall (r c : F) (a : t G 1) (c r : t F 1),
+(a; c; r) = (schnorr_simulator g h r c) ->
+accepting_conversation g h (a; c; r) = true.
+Proof using -(x R). (* terms omitted *) Qed.
+
+Lemma special_soundness: 
+forall (a : G) (ca ra cb rb : F), ca <> cb ->
+accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
+accepting_conversation g h ([a]; [cb]; [rb]) = true ->
+exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
+Proof using -(x R). (* proof terms omitted *) Qed.
+
+\end{lstlisting}
+
+  \subsection{Uniform Distribution}
+  To reason about special honest-verifier zero-knowledge proof 
+  intuitively, we need a model of uniform distribution. 
+  we encode distribution a list of tuples where the 
+  second element of tuple basically is probability of first element 
+  in the tuple. Moreover, we define equality on distribution by 
+  stating that two distributions are equal if they are permutation 
+  of each other. Finally, we define a function , $uniform\_with\_replacement$, 
+  to generate uniform distributions.
+
+  \begin{lstlisting}[language=Coq]
+
+(* Probability Distribution on a type A *)
+Definition dist (A : Type) : Type := list (A * prob).
+
+(* Uniform distribution u*)
+Definition uniform_with_replacement {A : Type} : 
+  forall (l : list A), l <> [] -> dist A.
+Proof.
+  intros ? H.
+  remember (Pos.of_nat (List.length l)) as len.
+  exact (List.map 
+    (fun x => (x, mk_prob 1 len)) l).
+Defined.
+\end{lstlisting}
+
+We prove that the dist is a monad (\textbf{Cite some work}) by 
+giving it a suitable definitions of ret and bind. Making 
+it an instance of monad makes our life easier because 
+we can compose a distribution $d$ $n$ times to 
+returns a distribution on a vector of $n$ elements.
+
+\begin{lstlisting}[language=Coq]
+(* Probability Monad *)
+Definition Ret {A : Type} (x : A) : 
+  dist A := [(x, one)].
+
+Fixpoint Bind {A B : Type} (xs : dist A)  
+  (f : A -> dist B) : dist B := 
+  match xs with 
+  | [] => [] 
+  | (ax, px) :: tx => 
+    List.append (List.map (fun '(ut, pt) => 
+    (ut, mul_prob px pt)) (f ax)) (Bind tx f)
   end.
 
+\end{lstlisting}
+
+Now we have all the ingredients to prove the zero-knowledge 
+proof of the Schnorr protocol. We define the 
+Schnorr distribution $schnorr\_distribution$
+that involves the secret $x$ and 
+the simulator distribution $simulator\_distribution$
+that does not involve the secret $x$. 
+In the Schnorr distibution we draw 
+a random field element $u$ from a uniform 
+distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
+and use this $u$ to construct a distribution; 
+similarly in the simulator distribution 
+we draw a random field element $u$ from 
+$uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
+and use it construct a distribution. Using these 
+two definitions, we prove that these two 
+distributions are identical 
+$special\_honest\_verifier\_zkp$. However, 
+contrary to informal reasoning, these two 
+distributions are not syntactically equal but 
+semantically equal. For both distributions, 
+the first component is a transcript $(a, c, r)$ and 
+the second component is a rational number that represents 
+its probability. The triples in both distrubtions 
+are an accepting transcript (semantic) but they 
+are not identical and differ syntactically; 
+therefore we first apply the 
+$accepting\_conversation$ to the first pair of 
+both distributions which turn them into 
+a boolean value (true). After this  
+application both distributions are identical 
+that we prove.
+
+\begin{lstlisting}[language=Coq]
 (* Distribution that involves the secret x *)
@@
   Ret (schnorr_simulator g h u c).
+
+Lemma special_honest_verifier_zkp : 
+  forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
+  List.map (fun '(a, p) => 
+    (accepting_conversation g h a, p))
+    (@schnorr_distribution lf Hlfn x g c) = 
+  List.map (fun '(a, p) => 
+    (accepting_conversation g h a, p))
+    (@simulator_distribution lf Hlfn g h c).
+Proof. (* proof terms omitted *) Qed. 
   \end{lstlisting}
 
-  Finally we establish the completeness, special soundness, 
-  and special honest-verifier zero-knowledge proof.
+We shown in the function $repeat\_dist\_ntimes\_vector$.
+  The reader can see from the proof 
+  $uniform\_probability\_multidraw\_prob$
+  that if a distribution $lf$ is repeated 
+  $n$ times then the probability of this distribution 
+  is $1/|lf|^n$. We use $repeat\_dist\_ntimes\_vector$ 
+  when we combine multiple sigma protocols and 
+  want to to prove zero-knowledge property. For example, 
+  in Parallel composition when we combine $n$ sigma protocol 
+  we need to need to draw a vector $n$ random numbers to 
+  prove the zero-knowledge property.
 
 \begin{lstlisting}[language=Coq]
-  Lemma schnorr_completeness : 
-    forall (r c : F) (a : t G 1) (c r : t F 1),
-    (a; c; r) = (schnorr_protocol x g r c) ->
-    accepting_conversation g h (a; c; r) = true.
-  Proof. (* proof terms omitted *) Qed.
-
-  Lemma simulator_completeness : 
-      forall (r c : F) (a : t G 1) (c r : t F 1),
-      (a; c; r) = (schnorr_simulator g h r c) ->
-      accepting_conversation g h (a; c; r) = true.
-    Proof using -(x R). (* proof terms omitted *) Qed.
-
-  Lemma special_soundness: 
-    forall (a : G) (ca ra cb rb : F), ca <> cb ->
-    accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
-    accepting_conversation g h ([a]; [cb]; [rb]) = true ->
-    (* then we can find a witness y such that g^y = h *)
-    exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
-  Proof using -(x R). (* proof terms omitted *) Qed.
-
-  (* it's identical, i.e., information theoretic zero-knowledge proof *)
-  (* Under the hood, it is modelled as a list and looks like:
-      [((a; c; r), prob); ((a; c; r), prob) ......].
-    We map accepting_conversation to crunch the first pair, 
-    (a, c, r), and produce boolean a value (true), 
-    and then we show that these two distribution are 
-    identical 
-  *)
-  Lemma special_honest_verifier_zkp : 
-    forall (lf : list F) (Hlfn : lf <> List.nil) (c : F), 
-    List.map (fun '(a, p) => (accepting_conversation g h a, p))
-      (@schnorr_distribution lf Hlfn x g c) = 
-    List.map (fun '(a, p) => (accepting_conversation g h a, p))
-      (@simulator_distribution lf Hlfn g h c).
-  Proof. (* proof terms omitted *) Qed.
-
-  \end{lstlisting}
-
-In our library, we have encoded Parallel composition, 
-AND composition, OR composition, EQ composition, and 
-NEQ composition. Below we explain the OR composition
-beause it is more involved than the rest.
-
-  However, we would like 
-  to emphasise that we worked in a vector-space, rather 
-  than concrete numbers. Working in (abstract) vector-space makes our system 
-  amenable to be instantiated by any group and field 
-  (Elliptic curve vs Concrete Nubmers). \textbf{Currently, 
-  our library comes with concrete nubmers but it can easily be 
-  instantiated with Elliptic curve cryptography}
-
-  \textbf{Coq code of Schnorr goes here}
-
-  The reader can see that we have used vector space. Now 
-  we establish completeness, (special) soundness, and zero-knowledge 
-  proof of knowledge (ZkPOK).
-
-  \textbf{Coq code soundness, completeness, zkp goes here}
-
-  The proof of completeness and soundness are fairly straightforward but 
-  zero-knowledge proof of knowledge requires probabilistic reasoning.
-
-  \textbf{Coq code goes here}
-
-  In our library, we have encoded Parallel composition, 
-  And composition, Or composition, EQ composition, and 
-  NEQ composition. Below we explain the OR composition
-  beause it is more involved than the rest.
-
-  \textbf{OR composition and Coq code}
-
-  \subsection{Uniform Distribution}
-  To reason about special honest-verifier zero-knowledge proof 
-  intuitively, we need a model of uniform distribution. 
-  we encode distribution a list of tuples where the 
-  second element of tuple basically is probability of first element 
-  in the tuple. Moreover, we define equality on distribution by 
-  stating that two distributions are equal if they are permutation 
-  of each other.
-
-  \begin{lstlisting}[language=Coq]
-
-  (* Probability Distribution on a type A *)
-  Definition dist (A : Type) : Type := list (A * prob).
-
-  Definition dist_equiv {A : Type} : relation (dist A) := 
-  fun xs ys => Permutation xs ys.
-
-  (* Probability Monad *)
-  Definition Ret {A : Type} (x : A) : dist A := [(x, one)].
-
-  Fixpoint Bind {A B : Type} (xs : dist A)  
-    (f : A -> dist B) : dist B := 
-    match xs with 
-    | [] => [] 
-    | (ax, px) :: tx => 
-      List.append (List.map (fun '(ut, pt) => 
-      (ut, mul_prob px pt)) (f ax)) (Bind tx f)
-    end.
-
-    (* Uniform distribution u*)
-    Definition uniform_with_replacement {A : Type} : 
-      forall (l : list A), l <> [] -> dist A.
-    Proof.
-      intros ? H.
-      remember (Pos.of_nat (List.length l)) as len.
-      exact (List.map 
-        (fun x => (x, mk_prob 1 len)) l).
-    Defined.
-
 Fixpoint repeat_dist_ntimes_vector {A : Type} 
-      (d : dist A) 
-      (n : nat) : dist (Vector.t A n) := 
+(d : dist A) (n : nat) : dist (Vector.t A n) := 
 match n with 
@@
 
-    Lemma uniform_probability_multidraw_prob {A : Type} :
-      forall n lf (a : Vector.t A n) b (Hlf : lf <> []), 
+Lemma uniform_probability_multidraw_prob 
+{A : Type} : forall n (lf : dist A) 
+(a : Vector.t A n) b (Hlf : lf <> []), 
 In (a, b) (repeat_dist_ntimes_vector 
@@
 (Nat.pow (List.length lf) n)).
+
+Definition parallel_schnorr_distribution  
+  {n : nat} (lf : list F) (Hlfn : lf <> List.nil) 
+  (x : F) (g : G) (cs : Vector.t F n) : 
+  dist (@sigma_proto n n n) :=
+  (* draw n random elements *)
+  us <- repeat_dist_ntimes_vector 
+    (uniform_with_replacement lf Hlfn) n ;;
+  Ret (construct_parallel_schnorr x g us cs).
 \end{lstlisting}
 
-  We use the $uniform\_probability\_multidraw\_prop$ theorem 
-  for special honest-verifier zero-knowledge proof.
+\subsection{Efficient Modular Arithmetic}
+ As we stated that our formalisation is  
+ abstract and can be instantiated with 
+ a suitable group and field. In order 
+ to run our code, we have developed 
+ a formally verified Schnorr group (\textbf{cite here}). 
+\begin{lstlisting}[language=Coq]
+Section SchnorrGroup. 
+  Context 
+    {k p q : Z}
+    {Hk : p = k * q + 1}
+    {Hp : prime p}
+    {Hq : prime q}.
+
+  Record Schnorr_group := 
+    mk_schnorr 
+    {v : Z; Ha : 0 < v < p; 
+    Hb : (v ^ q mod p = 1)}.
+
+  (* Neutral Element *)
+  Definition one : Schnorr_group.
+    refine 
+      (mk_schnorr 1 one_mod_p 
+      one_pow_mod_q).
+  Defined.
+
+  Definition mul_schnorr_group 
+      (u v : Schnorr_group) : Schnorr_group.
+  refine(
+    match u, v with 
+    | mk_schnorr au Hua Hub, 
+      mk_schnorr av Hva Hvb => 
+      mk_schnorr (Z.modulo (au * av) p) 
+      (@multiplication_bound p Hp au 
+      av Hua Hva)  _
+    end).
+  Defined.
+
+  (* u ^ (p - 2) is inverse of u *)
+  Definition inv_schnorr_group 
+  (u : Schnorr_group) : Schnorr_group.
+  refine(
+    match u with 
+    | mk_schnorr au Hu Hv => mk_schnorr
+        (Z.of_N (Npow_mod (Z.to_N au) 
+        (Z.to_N (p - 2)) (Z.to_N p)))
+        (@inv_schnorr_group_first au Hu)
+        (inv_schnorr_group_second au Hu Hv)
+    end).
+  Defined.
+
+  (* Schnorr is a commutative Group *)
+  Global Instance schnorr_comm : 
+    @commutative_group 
+    Schnorr_group (@eq Schnorr_group) 
+    mul_schnorr_group one inv_schnorr_group.
+  Proof. ... Qed.
+
+\end{lstlisting}
+
+Similarly, we have encoded a prime field.
 
@@
 
-(* schnorr distribution *)
-    Definition generalised_or_schnorr_distribution  
-      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
-      (x : F) (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
-      dist (@sigma_proto (m + (1 + n)) 
-        (1 + (m + (1 + n))) (m + (1 + n))) :=
-      (* draw ((m + (1 + n)) + (m + n)) random elements *)
-      usrs <- repeat_dist_ntimes_vector 
-        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
-      Ret (construct_or_conversations_schnorr x gs hs usrs c).
+(* Prime Field *)
+Section ZpField.
 
-    (* simulator distribution *)
-    Definition generalised_or_simulator_distribution  
-      {n m : nat} (lf : list F) (Hlfn : lf <> List.nil) 
-      (gs hs : Vector.t G (m + (1 + n))) (c : F) : 
-      dist (@sigma_proto (m + (1 + n)) 
-        (1 + (m + (1 + n))) (m + (1 + n))) :=
-      (* draw ((m + (1 + n)) + (m + n)) random elements *)
-      usrs <- repeat_dist_ntimes_vector 
-        (uniform_with_replacement lf Hlfn) ((m + (1 + n)) + (m + n)) ;;
-      Ret (construct_or_conversations_simulator gs hs usrs c).
+  Context 
+    {p : Z}
+    {Hp : prime p}.
+
+  Record Zp := 
+    mk_zp {v : Z; Hv : Z.modulo v p = v}.
+
+  Definition zp_inv (x : Zp) : Zp.
+    refine (match x with
+      | mk_zp ax Hu => mk_zp 
+        (Z.modulo 
+          (Z.of_N (Npow_mod (Z.to_N ax) 
+          (Z.to_N (p - 2)) (Z.to_N p)))
+          p) _ 
+    end).
+    rewrite Zmod_mod.
+    exact eq_refl.
+  Defined.
+
+  Definition zp_div (x y : Zp) : Zp :=
+    zp_mul x (zp_inv y).
 
@@
 
-  \subsection{Efficient Modular Arithmetic}
-  In order to call the functions from our formalisation, 
-  a user need to instantiate
+Finally, we prove that they form a vector space. 
+We have encoded the scalar mulitplication of 
+vector space as a pow function that takes an element from 
+a Schnorr group and an element from 
+a given field and returns an element in the 
+Schnorr group.  The reader can see that our encoding eliminates all 
+possibilities of mixing group and field, both represented 
+as an integer modulo some large 
+prime \cite{10.1007/978-3-662-63958-0_24}.
+
+\begin{lstlisting}[language=Coq]
+
+  Definition pow (g : @Schnorr.Schnorr_group p q) 
+  (y : @Zpfield.Zp q) : @Schnorr.Schnorr_group p q.
+  refine 
+    match g, y with 
+    | mk_schnorr gt Hgta Hgtb, Zpfield.mk_zp yt Hyt => 
+      mk_schnorr  
+      (Z.of_N (Npow_mod (Z.to_N gt) (Z.to_N yt) (Z.to_N p))) 
+      (pow_subproof_first gt yt Hgta Hyt)
+      (pow_subproof_second _ _  Hyt Hgta Hgtb)
+    end.
+  Defined.
+
+  Global Instance pow_vspace : 
+  @vector_space 
+    (* Field *)
+    (@Zpfield.Zp q) (@eq (@Zpfield.Zp q))
+    (@Zpfield.zero q Hq) (@Zpfield.one q Hq)
+    (@Zpfield.zp_add q) (@Zpfield.zp_mul q)
+    (@Zpfield.zp_sub q) (@Zpfield.zp_div q)
+    (@Zpfield.zp_opp q Hq) (@Zpfield.zp_inv q)
+    (* Vector *)
+    (Schnorr_group p q) (@eq (Schnorr_group p q))
+    (@one p q Hp Hq) 
+    (@inv_schnorr_group k p q Hk Hp Hq)
+    (@Schnorr.mul_schnorr_group p q Hp Hq)
+    pow.
+
+\end{lstlisting}
 
@@
  properties.
+
+\section{MetaCoq}
+  Bas Spitters
 

### 2024-05-29 paper/IEEES/paper.tex
Added Coq introduction and soundess of schnor

@@
 allows for the verification of the election results by checking the proofs of correctness 
-only after the election has concluded. This ensures that the election process was conducted 
-properly and that the results are accurate, but it is applied after the voting has taken place.
-The question arises: can we use it before an election?
+once the election has concluded. This ensures that the election process was conducted 
+properly and that the results are accurate, but it is applied during or after the voting has taken place.
+However, can we use it before an election?
 The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
-it and develop various components of electronic voting 
-software in this formal language. This process is called as formal verification and it ensures 
-that the software always produces valid proofs, 
+it, and develop various components of electronic voting 
+software in this formal language. This process is called as  formal verification, or correct-by-construction,
+and it ensures that the software always produces valid proofs, 
 which are consistently accepted by voters and scrutineers. In other words, formal verification
@@
 
-In this paper, we present a certified implementation of the Sigma protocol --an efficient 
+In this paper, we present a certified implementation of sigma protocol --an efficient 
 type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
-the formal language of Coq proof assistant. Given that the formal language of Coq 
-is constructive, we get an implementation that can be executed on a computer.
-
+the formal language of Coq proof assistant. 
 We have formalised and analysed the interactive version of 
@@
 our library. Unlike Helios and SwissPost,
-we write one implementation and extract WebAssembly (front-end) and Rust (back-end). 
+we write one implementation and extract WebAssembly (front-end) and Rust (back-end) (\textbf{using the MetaCoq library}).
 Belenois is slightly different in this respect and uses Js\_of\_ocaml 
@@
 \subsection{Outline}
+The rest of the paper is organised as follows: in section \ref{sigma_protocol}
+we explain sigma protocol and its security properties.
 
-\section{Sigma Protocol}
+\section{Sigma Protocol}\label{sigma_protocol}
 Despite the recent growth and popularity of zero-knowledge succinct 
@@
 
-\section{Coq formalisation}
+\section{The Coq Theorem Prover}
+\textbf{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
+can explain MetaCoq here as well and the extraction to Rust and WebAssembly
+so that it justifies this tutorial}
+The Coq theorem prover \cite{the_coq_development_team} is a computer program that interacts with users, 
+enabling them to encode mathematical definitions, express specifications (true statements) about 
+these definitions, and formally prove that the definitions imply the specifications. 
+A user first defines their mathematical object (definition) and then figure 
+out some  true statements (specifications) about 
+that object. Once the user has definition 
+and specifications, they need to prove 
+that the definition satisfies the specifications 
+(proof writing). In general, amongst these three steps, 
+the proof writing step is the most challenging and important step. 
+During the proof writing, the user interacts with the Coq theorem prover 
+via \emph{tactics}, a domain specific language 
+to ease the proof writing. Even though the Coq theorem 
+provides some amount of automation and proof 
+search, most of the time it requires human assistance to finish the proof. 
+It is one the most popular and robust theorem, and
+one of reasons for its popularity is 
+dependent types, that makes it possible to encode
+any mathematical statement in its logic.
+It has been used to verify many real world software projects and mathematical 
+artefacts. For example, Coq has been used to 
+formally verify CompCert \cite{10.1145/1111037.1111042}, 
+a C compiler used by many companies\footnote{https://www.absint.com/partners.htm}, 
+Fiat-Crypto \cite{8835346} 
+used in BoringSSL --a cryptographic library used in Chrome, Android, 
+and CloudFlare--, ConCert \cite{10.1145/3372885.3373829}, 
+a smart contract certification framework, etc. \textbf{FIXME: More examples}
+
+\subsubsection*{Definitions, Specifications, and Proofs}
+In this section, we demonstrate how to encode definitions, write specifications,
+and formally prove that definitions satisfy the specifications 
+in the Coq theorem prover by an example of 
+natural numbers (natural numbers is the set $\{0, 1, 2, 3, \dots \}$). 
+The set of natural numbers $Nat$ is the set of elements defined by the 
+following clauses:
+\begin{itemize}
+  \item \emph{Zero}, represents $0$, is in the set Nat ($Zero \in Nat$)
+  \item if $n$ is in the set Nat, then \emph{Succ n}, represents $n + 1$, 
+    is also in the set Nat (if $n \in Nat$, then $Succ \text{ }n \in Nat$)
+\end{itemize}
+
+\noindent 
+This representation of natural numbers is called 
+inductively defined set where the base case, or starting point,
+is Zero (constant symbol), and if we have a natural number $n$, then we can 
+get the next natural number by prefixing Succ (unary function symbol) to $n$.  
+Using this encoding of natural numbers, we can represent 
+$1$ by \emph{Succ Zero}, and $2$ by \emph{Succ (Succ Zero)}, 
+and so on. We encode the set \emph{Nat} in Coq as inductively defined data type, 
+shown in Listing \ref{ind_nat}, with 
+two constructors: \emph{Zero} and \emph{Succ}. 
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
+Inductive Nat : Type := 
+| Zero : Nat 
+| Succ : Nat -> Nat.
+\end{lstlisting}
+
+With the definition of natural numbers at our disposal,
+we can define addition, subtraction, multiplication, division, and 
+many other mathematical functions on natural numbers in the Coq theorem prover. 
+However, we only define the addition function,
+shown in Listing \ref{add_fn}, to demonstrate the concept. 
+In Coq, \emph{Fixpoint} is a keyword 
+for defining function, followed by the name of the function (\emph{plus}), 
+arguments (\emph{m} and \emph{n}), and the body (definition) of the function.
+The body of plus shown in Listing \ref{add_fn} is Coq encoding of the 
+following two clauses:
+\begin{enumerate}
+  \item plus Zero n = n 
+  \item plus (Succ m) n = Succ (plus m n)
+\end{enumerate}
+
+\noindent 
+The first clause amounts to $0 + n = n$ and the second clause
+amounts to $ (1 + m) + n = 1 + (m + n)$.
+
+\begin{lstlisting}[frame=single, language=Coq, caption={Addition of two Natural Numbers},
+  label={add_fn},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
+Fixpoint plus (m n : Nat) :=
+  match m with
+  | Zero => n
+  | Succ m' => Succ (plus m' n)
+  end.
+
+\end{lstlisting}
+
+So far we have just definitions of natural numbers and addition on them.
+Now, it is time to define some specification (true statement) about
+the addition operation, on natural numbers. From mathematical 
+literature, we know that the addition operation on natural
+numbers is associative and commutative. For simplicity, we
+prove that our definition of addition on natural numbers is commutative, shown in 
+Listing \ref{plus_comm}, and it is precisely the \emph{specification} for 
+our addition operation.
+
+\begin{lstlisting}[frame=single, language=Coq, caption={Addition is Commutative},
+  label={plus_comm},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
+Theorem plus_commutative : 
+  forall n m, plus n m = plus m n. 
+Proof.
+  induction n.
+  (* base case *)
+  + intros m.
+  (* proof terms omitted *)
+  (* inductive case *)  
+  + intros m.
+    rewrite IHn.
+    (* proof terms omitted *)
+Qed.
+
+\end{lstlisting}
+
+In Coq, \emph{Theorem} is the keyword
+to define a specification, followed by the name (\emph{plus\_comm}). 
+It says that for any two arbitrary natural numbers $m$ and $n$, 
+encoded as \texttt{forall n m}, adding $n$ and $m$ is the same
+as adding $m$ and $n$, encoded as \texttt{plus n m = plus m n}.
+To write a formal proof of this statement, we tell the Coq theorem 
+prover that we want to use the tactic language by 
+stating the keyword \emph{Proof}. After finishing the proof, 
+we use the keyword \emph{Qed} to inform Coq that our proof is 
+finished. The moment Coq sees \emph{Qed},
+it ensures that the proof is complete and correct according to its 
+underlying logic. If we try to use Qed without finishing the proof,
+Coq will not let us do so. Therefore, once we have Qed for any 
+specification, by just trusting the Coq theorem prover we can be 
+sure that our proof is correct. However, at this point, 
+the curious reader can argue that why should we trust 
+Coq because it is a computer program, similar any other 
+computer program? Trusting Coq hinges on two things: 
+(i) the meta theory, \emph{Calculus of Inductive Construction},
+of Coq \cite{thierry1988calculus}
+and (ii) its OCaml implementation \cite{the_coq_development_team}.
+The meta theory of Coq has been scrutinised for decades
+by many mathematicians and so far it has withstood all 
+the scrutiny. The OCaml implementation of Coq  has a very 
+small kernel and has been inspected by many computer scientists. 
+In addition, there is a recent effort to develop more 
+rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
+to state that we are following this path of MetaCoq}.
+
+The keywords \emph{induction, intros, rewrite}
+are tactics that are used to prove the statement that addition 
+on natural numbers is commutative. 
+The proof written between 
+the keywords \emph{Proof} and \emph{Qed} amounts to the following: 
+\begin{itemize}
+  \item Base case: when $n$ is Zero, we need to prove that \texttt{plus Zero m = plus m Zero}
+  \item Inductive case: when $n$ is Succ, we assume \texttt{plus m n = plus n m} 
+      and we need to prove \texttt{plus (Succ m) n = plus n (Succ m)}
+\end{itemize}  
+\noindent
+It is called proof by induction, and 
+tactics are used to make the complicated 
+process of proof writing easy.
+
+\subsection{Schnorr Protocol Coq Encoding}
 
@@
   \begin{itemize}
-    \item the prover picks a random number $u$, computes $c = g^u$,
-    and sends $c$ to the verifier.
-    \item the verifier picks a random challenge $e$ and sends it to
+    \item the prover picks a random number $u$, computes $a = g^u$,
+    and sends $a$ to the verifier.
+    \item the verifier picks a random challenge $c$ and sends it to
     the prover
-    \item the prover computes $t = u + e * w$ and sends $t$ to the
+    \item the prover computes $r = u + c * w$ and sends $r$ to the
     verifier
@@
 
-The verifier accepts if $g^t = c * h^e$, otherwise rejects. We can prove that 
+The verifier accepts the transcript $(a, c, r)$ if $g^r = a * h^c$, otherwise rejects. We can prove that 
 this protocol has completeness, special soundness, and special honest-verifier 
@@
   \item completeness: when $P$ and $V$ both follows the protocol, $V$ accepts the proof, i.e., 
-  the verification equation checks. We can see by algebraic simplification that is the case.
+  the verification equation checks out. We can see by algebraic simplification that it is the case.
     \begin{align*}
-      g^t = g^{u + e * w} = g^u * (g^w)^e = c * h^e
+      g^r = g^{u + c * w} = g^u * (g^w)^c = a * h^c
     \end{align*}
-  \item special soundness:
+  \item special soundness: from two accepting 
+  conversations $(a, c, r)$ and $(a, c', r')$ where $c \neq c'$,
+  a polynomial-time extractor can extract a witness $w$, 
+  which is equal to $(r - r') * (c - c')^{-1}$, 
+  such that $g^w = h$. By means of algebraic simplification, 
+  we can see that it is the case.  
+  \begin{align}
+    g^r = a * h^c = g^u * (g^w)^c = g^{u + w * c}  \\
+    g^{r'} = a * h^{c'} = g^u * (g^w)^{c'} = g^{u + w * c'}
+  \end{align}
+  Diving the expression (1) with (2), we get
+  \begin{align*}
+    g^{(r-r')} = g^{w * (c - c')}
+  \end{align*}
+  and multiplying both sides by $(c - c')^{-1}$ we 
+  get 
+  \begin{align*}
+    g^{(r-r') * (c - c')^{-1}} = g^{w}
+  \end{align*}
 
@@
 
-\begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Schnorr protocol},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 (*Real transcript (involves secret x)*)
-Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
- sigma_proto :=  ([g^u]; [c]; [u + c * x]).
+Definition schnorr_protocol (x : F) (g : G) 
+ (u c : F) : sigma_proto :=  
+ ([g^u]; [c]; [u + c * x]).
 
 (*Fake transcript (without the witness x)*)
-Definition schnorr_simulator (g h : G) (u c : F) :
-  sigma_proto := ([gop (g^u) (h^(opp c))]; [c]; [u]).
+Definition schnorr_simulator (g h : G) 
+ (u c : F) : sigma_proto := 
+ ([gop (g^u) (h^(opp c))]; [c]; [u]).
 
-(*This function checks if a transcript 
-(a; c; r) is accepting or not. It checks
-if g^r = a * h^c*)
-Definition accepting_conversation 
-  (g h : G) (v : sigma_proto) : bool :=
+(*This function checks if a transcript (a; c; r) 
+is accepting or not. It checks if g^r = a * h^c*)
+Definition accepting_conversation (g h : G) 
+ (v : sigma_proto) : bool :=
  match v with
@@
 We prove the completeness and special soundness property of the Schnorr protocol, 
-as shown in the figure .... We however cannot prove the special honest-verifier 
+as shown in Lisitng \cite{comp_sound}. We however cannot prove the special honest-verifier 
 zero-knowledge property yet because it requires reasoning about probability that 
@@
 
-\begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Completeness and Soundness},
+  label={comp_sound},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 Lemma schnorr_completeness : 
@@
 forall (a : G) (ca ra cb rb : F), ca <> cb ->
-accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
-accepting_conversation g h ([a]; [cb]; [rb]) = true ->
+accepting_conversation g h ([a]; [ca]; [ra]) ->  
+accepting_conversation g h ([a]; [cb]; [rb]) ->
 exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
@@
 
-  \begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+    label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+    abovecaptionskip=-\medskipamount]
 
@@
 
-\begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 (* Probability Monad *)
@@
 
-\begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 (* Distribution that involves the secret x *)
@@
 
-\begin{lstlisting}[language=Coq]
+  \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+    label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+    abovecaptionskip=-\medskipamount]
 Fixpoint repeat_dist_ntimes_vector {A : Type} 
@@
  a formally verified Schnorr group (\textbf{cite here}). 
-\begin{lstlisting}[language=Coq]
+ \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 Section SchnorrGroup. 
@@
 
-\begin{lstlisting}[language=Coq]
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
 
@@
 
-\section{MetaCoq}
-  Bas Spitters
-
-\section{Web Assembly and Rust from the Coq Formalisation}
+\section{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
   Bas Spitter
@@
 
-\section{Related Work}
+\section{Related Work, Future Work, and Limitations}
   There are three work. Giles Barthe does not extract to executable code, 
@@
 
-\section{Conclusion, Future Work, and Limitations}
   In this paper, we present a certified implementation 

### 2024-06-03 paper/IEEES/paper.tex
more text

@@
 \usepackage{listings}
+\usepackage{tikz}
+\usetikzlibrary{positioning, arrows.meta}
 \usepackage{url}
@@
 interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
-\textit{Sigma protocol}, \textbf{shown in the figure }, is an efficient three move zero-knowledge proof where the 
+\textit{Sigma protocol}, shown in the figure \ref{fig:sig_picture}, is an efficient three move zero-knowledge proof where the 
 verifier is assumed to be honest and characterised by completeness, (special) soundness, and 
@@
 
-\textbf{Draw a picture here of sigma protocol}
+\begin{figure}[ht]
+  \centering
+\begin{tikzpicture}
+  \node (Prover)  {\textit{P (x, w)}} (0,0);
+  \node (Verifier) [right=of Prover] at (4, 0) {\textit{V(x)}};
+  % First arrow (left to right)
+  \draw[->] (0,-0.5) -- (5,-0.5) node[midway, above] {\textit{commitment}};
+
+  % Second arrow (right to left)
+  \draw[->] (5,-1) -- (0,-1) node[midway, above] {\textit{challenge}};
+
+  % Third arrow (left to right)
+  \draw[->] (0,-1.5) -- (5,-1.5) node[midway, above] {\textit{response}};
+\end{tikzpicture}
+\caption{Sigma Protocol}
+\label{fig:sig_picture}
+\end{figure}
 
@@
 enabling them to encode mathematical definitions, express specifications (true statements) about 
-these definitions, and formally prove that the definitions imply the specifications. 
+their definitions, and formally prove that the definitions imply the specifications. 
 A user first defines their mathematical object (definition) and then figure 
@@
 the proof writing step is the most challenging and important step. 
-During the proof writing, the user interacts with the Coq theorem prover 
+During the proof writing, an user interacts with the Coq theorem prover 
 via \emph{tactics}, a domain specific language 
@@
 
-So far we have just definitions of natural numbers and addition on them.
-Now, it is time to define some specification (true statement) about
-the addition operation, on natural numbers. From mathematical 
-literature, we know that the addition operation on natural
-numbers is associative and commutative. For simplicity, we
-prove that our definition of addition on natural numbers is commutative, shown in 
-Listing \ref{plus_comm}, and it is precisely the \emph{specification} for 
-our addition operation.
+So far, we have defined natural numbers and addition. Now, we will specify 
+some properties of addition on natural numbers. Mathematically, addition 
+is known to be associative and commutative. For simplicity, we will 
+prove that our addition definition is commutative, as shown in 
+Listing \ref{plus_comm}, which serves as the specification for our 
+addition operation.
 
@@
 
-In Coq, \emph{Theorem} is the keyword
-to define a specification, followed by the name (\emph{plus\_comm}). 
-It says that for any two arbitrary natural numbers $m$ and $n$, 
-encoded as \texttt{forall n m}, adding $n$ and $m$ is the same
-as adding $m$ and $n$, encoded as \texttt{plus n m = plus m n}.
-To write a formal proof of this statement, we tell the Coq theorem 
-prover that we want to use the tactic language by 
-stating the keyword \emph{Proof}. After finishing the proof, 
-we use the keyword \emph{Qed} to inform Coq that our proof is 
-finished. The moment Coq sees \emph{Qed},
-it ensures that the proof is complete and correct according to its 
-underlying logic. If we try to use Qed without finishing the proof,
-Coq will not let us do so. Therefore, once we have Qed for any 
-specification, by just trusting the Coq theorem prover we can be 
-sure that our proof is correct. However, at this point, 
-the curious reader can argue that why should we trust 
-Coq because it is a computer program, similar any other 
-computer program? Trusting Coq hinges on two things: 
-(i) the meta theory, \emph{Calculus of Inductive Construction},
-of Coq \cite{thierry1988calculus}
-and (ii) its OCaml implementation \cite{the_coq_development_team}.
+In Coq, \emph{Theorem} is the keyword used to define a specification, 
+followed by the name (\emph{plus\_comm}). This specifies that for any 
+two natural numbers $m$ and $n$ (encoded as \texttt{forall n m}), 
+adding $n$ to $m$ is the same as adding $m$ to $n$ 
+(encoded as \texttt{plus n m = plus m n}).
+To write a formal proof of this statement, we start by indicating that 
+we will use the tactic language with the keyword \emph{Proof}. Once the 
+proof is complete, we use the keyword \emph{Qed} to signal to Coq that 
+our proof is finished. At this point, Coq verifies that the proof is complete 
+and correct according to its logic. If the proof is not finished, Coq will 
+not accept \emph{Qed}. Therefore, having a \emph{Qed} for any specification 
+ensures that our proof is correct, provided we trust the Coq theorem prover.
+However, at this point, the curious reader can argue that why should we trust 
+Coq because it is a computer program, similar any other computer program? 
+Trust in Coq relies on two factors: (i) its meta-theory, the 
+\emph{Calculus of Inductive Constructions} \cite{thierry1988calculus}, and 
+(ii) its implementation in OCaml \cite{the_coq_development_team}.
 The meta theory of Coq has been scrutinised for decades
 by many mathematicians and so far it has withstood all 
-the scrutiny. The OCaml implementation of Coq  has a very 
-small kernel and has been inspected by many computer scientists. 
-In addition, there is a recent effort to develop more 
+the scrutiny, but not so much for its OCaml implementation \cite{coq_critical_bugs}. 
+Therefore, there is a recent effort to develop more 
 rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
-to state that we are following this path of MetaCoq}.
+to state that we are following this path of MetaCoq and extraction}.
 
-The keywords \emph{induction, intros, rewrite}
-are tactics that are used to prove the statement that addition 
-on natural numbers is commutative. 
-The proof written between 
-the keywords \emph{Proof} and \emph{Qed} amounts to the following: 
-\begin{itemize}
-  \item Base case: when $n$ is Zero, we need to prove that \texttt{plus Zero m = plus m Zero}
-  \item Inductive case: when $n$ is Succ, we assume \texttt{plus m n = plus n m} 
-      and we need to prove \texttt{plus (Succ m) n = plus n (Succ m)}
-\end{itemize}  
-\noindent
-It is called proof by induction, and 
-tactics are used to make the complicated 
-process of proof writing easy.
+\subsection{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
+  Bas
 
 \subsection{Schnorr Protocol Coq Encoding}
-
-  We briefly explain the Schnorr protocol, which is very similar to figure \textbf{refer here to sigma protocol picture}.
-  Given some public input $(G, g, q, h)$ where $G$
+  We briefly explain the Schnorr protocol, an interactive protocol 
+  between a prover and a verifier, which follows the same structure as 
+  depicted in Figure \ref{fig:sig_picture}. 
+  Given some public input $G = (g, q, h)$ where $G$
   is a cyclic group of prime order $q$, $g$ and $h$ are two 
@@
   \item special honest-verifier zero-knowledge proof:
+   the distribution for the conversations with an honest verifier --involving witness $w$--
+   and the conversation with a simulator --without witness $w$-- are the same, given a 
+   challenge $c$. We can 
+   see this algebraically that both distributions \ref{f} and \ref{snd} have the identical 
+   distribution, i.e., $1/q$. 
+   \begin{align}\label{f}
+    \{(a, c, r) \mid u \in_{R} Z_q ; a := g^u; r := u + c * w \}
+   \end{align}
+   \begin{align}\label{snd}
+    \{(a, c, r) \mid u \in_{R} Z_q ; a := g^r * h^{-c}\}
+   \end{align}
 
@@
 
-In the Schnorr protocol, $g, h, c$ are group elements from underlying group, while 
-$u, e, t$ are scalar values from underlying prime field. In practice, 
-both the group elements and the fields elements are some large prime numbers,
-albeit the operations differ. For most of the languages it does not matter, 
-but also a potential source of bugs (cite thomas work here). However, 
-we need to flesh down all the details while encoding it Coq. One possibility is 
-to encode the Coq functions to work with concrete numbers but this leads to 
-cumbersome proofs because of dealing with concrete numbers. In our formalisation, 
+In the Schnorr protocol, the elements $g$, $h$, and $a$ are group elements from the underlying group, while $u$, $c$, and $r$
+are scalar values from the underlying prime field. In practice, both the group elements and the field elements are large 
+numbers modulo some prime numbers, although the operations on them differ. 
+One possibility is to encode the Coq functions to work with concrete numbers from the underlying group and field, 
+but this leads to cumbersome proofs because of dealing with concrete numbers, but the bigger problem 
+is that it is not modular. For most programming languages, this distinction 
+may not be significant, but it can be a potential source of bugs \cite{10.1007/978-3-662-63958-0_24}. 
+However, when encoding it in Coq, we need to thoroughly detail these distinctions because 
+the same large number can belong to a group or field and that dictates what operations are available for them. 
+Therefore, to avoid this unpleasant situation,  
 we decided to abstract the underlying group as an abstract type $G$, endowed with 
 usual group operation, and the underlying field as an abstract type $F$, endowed with 
-filed operation. Finally, we abstract these two types in an vector space. This 
+filed operation in our formalisation. Moreover, we abstract these two types into a vector space for smooth interaction between 
+group element and field element (exponential needs this). This 
 makes our formalisation generic that can be instantiated with 
@@
 vector space. For example, in our formalisation we have developed 
-efficient algorithm for Schnorr group but our formalisation can 
+efficient algorithm for the Schnorr group but our formalisation can 
 later be also instantiated with elliptic curve group. However, 
@@
 which can be easily automated. Therefore, we model the Schnorr 
-protoco, the simulator, and the verification equation in Coq as follows:
+protocol, the simulator, and the verification equation in Coq as follows:
 
@@
  where $F$ is the underlying field, $G$ is the underlying group,
- $+ : F \rightarrow F \rightarrow F$ is field addition,
- $* : F \rightarrow F \rightarrow F$ is field multiplication, and
- $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ scalar multiplication of vector space.  
+ $+ : F \rightarrow F \rightarrow F$ is the field addition,
+ $* : F \rightarrow F \rightarrow F$ is the field multiplication, 
+ $gop : G \rightarrow G \rightarrow G$ is the group operation, and
+ $\mbox{\textasciicircum}: G \rightarrow F \rightarrow G$ is the scalar multiplication of vector space.  
  Recall that a vector space consists of a set of 
@@
 We prove the completeness and special soundness property of the Schnorr protocol, 
-as shown in Lisitng \cite{comp_sound}. We however cannot prove the special honest-verifier 
-zero-knowledge property yet because it requires reasoning about probability that 
-we discuss in the next section.
+as shown in Listing \cite{comp_sound}. However, to prove the special honest-verifier 
+zero-knowledge property we need a model to reason about uniform probability 
+distribution in Coq. We discuss the encoding of uniform probability distribution 
+in the next section and subsequently explain the special honest-verifier zero-knowledge
+proof.
 
@@
 intuitively, we need a model of uniform distribution. 
-  we encode distribution a list of tuples where the 
+We follow the \cite{erwig2006functional}  and 
+encode the distribution a list of tuples where the 
 second element of tuple basically is probability of first element 
@@
 stating that two distributions are equal if they are permutation 
-  of each other. Finally, we define a function , $uniform\_with\_replacement$, 
-  to generate uniform distributions.
-
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
-    label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
-    abovecaptionskip=-\medskipamount]
-
-(* Probability Distribution on a type A *)
-Definition dist (A : Type) : Type := list (A * prob).
-
-(* Uniform distribution u*)
-Definition uniform_with_replacement {A : Type} : 
-  forall (l : list A), l <> [] -> dist A.
-Proof.
-  intros ? H.
-  remember (Pos.of_nat (List.length l)) as len.
-  exact (List.map 
-    (fun x => (x, mk_prob 1 len)) l).
-Defined.
-\end{lstlisting}
-
-We prove that the dist is a monad (\textbf{Cite some work}) by 
+of each other. This encoding is flexible and allows us 
+to encode any kind of distribution. We prove that the dist is a 
+monad \cite{erwig2006functional} by 
 giving it a suitable definitions of ret and bind. Making 
@@
 returns a distribution on a vector of $n$ elements. 
+However, to reason about cryptographic primitives, we need uniform 
+distribution and therefore we define a function, $uniform\_with\_replacement$, 
+to generate uniform distributions, shown in Listing \ref{prob_def}.
+We prove various prop
 
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
-  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Uniform Probability Distribution},
+    label={prob_def},captionpos=t, basicstyle=\ttfamily\footnotesize,
     abovecaptionskip=-\medskipamount]
+(* Probability Distribution on a type A *)
+Definition dist (A : Type) : Type := 
+ list (A * prob).
+
 (* Probability Monad *)
@@
 
+(* Uniform distribution *)
+Definition uniform_with_replacement {A : Type} : 
+  forall (l : list A), l <> [] -> dist A.
+Proof.
+  intros ? H.
+  remember (Pos.of_nat (List.length l)) as len.
+  exact (List.map 
+    (fun x => (x, mk_prob 1 len)) l).
+Defined.
 \end{lstlisting}
 
-Now we have all the ingredients to prove the zero-knowledge 
-proof of the Schnorr protocol. We define the 
+Now we have all the ingredients to prove special honest-verifier 
+zero-knowledge proof of the Schnorr protocol. We define the 
 Schnorr distribution $schnorr\_distribution$
@@
 In the Schnorr distibution we draw 
-a random field element $u$ from a uniform 
-distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
-and use this $u$ to construct a distribution; 
-similarly in the simulator distribution 
+a random field element $u$ from the uniform 
+distribution $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$,
+where $lf$ is list of elements from which $u$
+is drawn and $Hlf$ is a proposition that 
+$lf$ is non-empty, and use it to construct 
+a distribution on sigma protocol. Similarly, 
+for the simulator distribution 
 we draw a random field element $u$ from 
 $uniform\_with\_replacement \text{ }lf \text{ } Hlfn$
-and use it construct a distribution. Using these 
-two definitions, we prove that these two 
+and use it construct a distribution on sigma protocol. 
+Using these two definitions, we prove that these two 
 distributions are identical 
 $special\_honest\_verifier\_zkp$. However, 
-contrary to informal reasoning, these two 
-distributions are not syntactically equal but 
+contrary to the reasoning in cryptographic papers, 
+these two distributions are not syntactically equal but 
 semantically equal. For both distributions, 
@@
 
-We shown in the function $repeat\_dist\_ntimes\_vector$.
-  The reader can see from the proof 
-  $uniform\_probability\_multidraw\_prob$
-  that if a distribution $lf$ is repeated 
-  $n$ times then the probability of this distribution 
-  is $1/|lf|^n$. We use $repeat\_dist\_ntimes\_vector$ 
-  when we combine multiple sigma protocols and 
-  want to to prove zero-knowledge property. For example, 
-  in Parallel composition when we combine $n$ sigma protocol 
+In the previous section, we explained the Schnorr proof, 
+but we have also formalised a way to combine $n$ And, Or, Eq, 
+and Parallel Schnorr statements. Proving special 
+honest-verifier zero-knowledge proof is more challenging 
+than a single Schnorr statement. One of the major challenge 
+is to draw $n$ random element for an uniform distribution 
+and therefore we have written the function $repeat\_dist\_ntimes\_vector$
+that takes a distribution $dist\text{ }A$ and a number $n$ and a returns 
+distribution of vectors of length $n$,  encoded as 
+$dist \text{ } (Vector.t \text{ } A \text{ } n)$. The 
+reader may notice that it is a generic function 
+where distribution can be instantiated with 
+any kind of distribution. However, in cryptography 
+we are mostly concerned with uniform distribution and  
+therefore in $uniform\_probability\_multidraw\_prob$ theorem
+we instantiate the distribution with 
+the uniform distribution $(uniform\_with\_replacement\text{ }lf\text{ }Hlf)$ and 
+prove that the probability of this distribution 
+is $1/|lf|^n$. We use it 
+in Parallel composition where we combine $n$ sigma protocol and  
 we need to need to draw a vector $n$ random numbers to 
-  prove the zero-knowledge property.
+prove the zero-knowledge property, as shown 
+in $parallel\_schnorr\_distribution$.
 
@@
 \subsection{Efficient Modular Arithmetic}
- As we stated that our formalisation is  
- abstract and can be instantiated with 
- a suitable group and field. In order 
- to run our code, we have developed 
- a formally verified Schnorr group (\textbf{cite here}). 
- \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+As stated earlier, to ensure the ease of proving, we worked with 
+an abstract vector space. However, to execute this code, we need to 
+instantiate the vector space with concrete examples. Therefore, we have 
+encoded a prime field and the Schnorr group \cite{schnorr1991efficient} (mulitplicative 
+group of integers modulo a large prime p) in the Coq theorem prover. 
+To encode the Schnorr group, we postulate three integer $k, p, \text{ and } q$. 
+Moreover, we assume $p \text{ and } q$ are primes where $p = k * q + 1$ (when 
+$k = 2$, these primes are called Sophie Germain primes). Finally, 
+we encode the neutral element $one$, the group multiplication $mul\_schnorr\_group$, 
+and the group inverse $inv\_schnorr\_group$. We prove that our encoding 
+of the Schnorr group in Coq is commutative group by making it 
+an instance of the typeclass $schnorr\_comm$, 
+which is an abstract typeclass that bundles the axioms 
+of commutative group.
+
+ \begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of the Schnorr Group},
   label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
@@
   Context 
-    {k p q : Z}
-    {Hk : p = k * q + 1}
-    {Hp : prime p}
-    {Hq : prime q}.
+    {k p q : Z} {Hk : p = k * q + 1}
+    {Hp : prime p} {Hq : prime q}.
 
-  Record Schnorr_group := 
-    mk_schnorr 
+  Record Schnorr_group := mk_schnorr 
     {v : Z; Ha : 0 < v < p; 
-    Hb : (v ^ q mod p = 1)}.
+    Hb : v ^ q mod p = 1}.
 
@@
       (u v : Schnorr_group) : Schnorr_group.
-  refine(
-    match u, v with 
-    | mk_schnorr au Hua Hub, 
-      mk_schnorr av Hva Hvb => 
-      mk_schnorr (Z.modulo (au * av) p) 
-      (@multiplication_bound p Hp au 
-      av Hua Hva)  _
-    end).
+  (* Proof terms omitted *)
   Defined.
@@
   Proof. ... Qed. 
-
+End SchnorrGroup.
 \end{lstlisting}
 
-Similarly, we have encoded a prime field.
+In order to encode prime field, we postulate an integer $p$ and 
+axiom that $p$ is prime. We encode the prime field as 
+a record $Zp$ that contains an integer $v$ with an axiom 
+that it is in the range of $[0 \ldots p)$. Moreover, 
+we define all the operation of $Zp$ and prove that 
+it is an instance of the typeclass $zp\_field$, which is 
+a typeclass that encodes the axioms of a field.
 
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
+\begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of Prime Field},
   label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
   abovecaptionskip=-\medskipamount]
-
 (* Prime Field *)
 Section ZpField.
+  Context 
+    {p : Z} {Hp : prime p}.
 
-  Context 
-    {p : Z}
-    {Hp : prime p}.
+  Record Zp := mk_zp 
+    {v : Z; Hv : Z.modulo v p = v}.
 
-  Record Zp := 
-    mk_zp {v : Z; Hv : Z.modulo v p = v}.
-
-  Definition zp_inv (x : Zp) : Zp.
-    refine (match x with
-      | mk_zp ax Hu => mk_zp 
-        (Z.modulo 
-          (Z.of_N (Npow_mod (Z.to_N ax) 
-          (Z.to_N (p - 2)) (Z.to_N p)))
-          p) _ 
-    end).
-    rewrite Zmod_mod.
-    exact eq_refl.
-  Defined.
-
-  Definition zp_div (x y : Zp) : Zp :=
-    zp_mul x (zp_inv y).
-
+  Global Instance zp_field : @field Zp zero 
+    one zp_opp zp_add zp_sub zp_mul zp_inv zp_div.
+End ZpField. 
 \end{lstlisting}
 
-Finally, we prove that they form a vector space. 
-We have encoded the scalar mulitplication of 
-vector space as a pow function that takes an element from 
+Finally, we combine the Schnorr group and the prime field 
+into a vector space instantiating the vector set with 
+the Schnorr group and the scalar set with the prime field. 
+However, in order to establish that it is an 
+instance of vector space we need the definition 
+of scalar mulitiplication. We encode the  
+the scalar mulitplication $pow$ of 
+vector space that takes an element from 
 a Schnorr group and an element from 
-a given field and returns an element in the 
+the prime field and returns an element in the 
 Schnorr group.  The reader can see that our encoding eliminates all 
@@
     match g, y with 
-    | mk_schnorr gt Hgta Hgtb, Zpfield.mk_zp yt Hyt => 
-      mk_schnorr  
-      (Z.of_N (Npow_mod (Z.to_N gt) (Z.to_N yt) (Z.to_N p))) 
-      (pow_subproof_first gt yt Hgta Hyt)
+    | mk_schnorr gt Hgta Hgtb, mk_zp yt Hyt => 
+      mk_schnorr  (Npow_mod gt yt p) 
+      (pow_subproof_first _ _ Hgta Hyt)
       (pow_subproof_second _ _ Hyt Hgta Hgtb)
@@
 
-\section{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
-  Bas Spitter
-
 \section{Case Studies/Experiment}
@@
 \section{Related Work, Future Work, and Limitations}
+  Given the popularity of sigma protocol in voting 
+  and other domains, it is not surprising that it has 
+  been formalised in the past \cite{5552642,9519460,
+  butler2021formalising,10.1145/3319535.3354247,287095,almeida2010certifying,10221929,
+  10.1145/3594735}.
+
+  Given the popularity of zero-knowledge in 
+  privacy presearving computation such as voting, cryptocurrencies, 
+  etc., it is not surprising that that sigma protocol and its other 
+  variant (zk-SNARK) are an active area of research
+
+  Given its popularity in voting, it is not surprising that 
+  Sigma protocol is an active area of research \cite{5552642}.
+
   There are three work. Giles Barthe does not extract to executable code, 

### 2024-06-06 paper/IEEES/paper.tex
More text

@@
 \usepackage{url}
+\usepackage{xcolor}
+\usepackage{soul}
 \usepackage{lstcoq}
@@
 \begin{abstract}
-  Despite the recent growth of zero-knowledge succinct argument 
-  of knowledge (ZkSNARK) in cryptocurrencies, 
-  sigma protocol remains a popular choice in electronic voting to maintain privacy 
+  \st{Despite the recent growth of zero-knowledge succinct argument 
+  of knowledge (ZkSNARK)}, 
+  $\Sigma$-protocol remains a popular choice in electronic voting to maintain privacy 
   and verifiability of elections and still used in prominent e-voting systems such as 
@@
   the existing implementations of sigma protocol have two 
-  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript)
+  shortcomings: (i) the same code is written twice, once for the front-end (JavaScript/TypeScript)
   and once for the back-end (Python/OCaml/Java), which is time-consuming but more importantly error-prone, 
@@
 
-  In this paper, we present a certified implementation of sigma protocol in the Coq proof assistant and
+  In this paper, we present a certified implementation of sigma protocol in the Coq theorem prover and
   prove our implementation is (special) sound, complete, and 
-  (honest verifier) zero-knowledge. Moreover, 
+  (special honest-verifier) zero-knowledge. Moreover, 
   we compile our Coq formalisation to WebAssembly and Rust; 
@@
   Helios, Belenois, and SwissPost voting systems. 
-  Our long terms goal is to provide a verified cryptographic library that can be 
-  readily used in privacy-preserving voting systems.
+  \st{Our long terms goal is to provide a verified cryptographic library that can be 
+  readily used in privacy-preserving voting systems.}
 \end{abstract}
@@
 they can streamline the voting process, reduce administrative burdens, and enable 
-faster tallying of results. However, the transition to electronic voting also brings significant 
-challenges, particularly in ensuring the privacy and verifiability of the voting process. Therefore, 
-privacy and verifiability are two crucial elements that a voting system must ensure to adhere with 
-the principles of a free-and-fair election. In a paper-ballot election, privacy is maintained by 
+faster tallying of results. However, electronic voting also brings significant 
+challenges in ensuring the privacy and verifiability, a must for free-and-fair elections, of the voting process. Therefore, 
+privacy and verifiability are two crucial elements that a voting system must ensure.
+In a paper-ballot election, privacy is maintained by 
 ensuring that no identifying information is present on a ballot that links it to a particular voter, 
@@
 the voting process. However, no matter how advanced the cryptographic techniques, they are useless 
-if their software implementation contains bugs.
-In fact, due to a major cryptographic flaw that
-could let someone change votes cast using Switzerland's online 
-voting software without being detected  \cite{9152765}, the Swiss Federal Chancellery suspended electronic voting in 
-2019. It only resumed in 2023 after getting feedbacks from academic 
-community \cite{swiss_evoting_chronik} about various component used in 
+if their software implementation contains bugs. In fact, 
+the Swiss Federal Chancellery suspended electronic voting in 2019 because of 
+a fatal software bug in the implementation of a cryptographic primitive 
+that allowed someone to change the cast votes without being detected \cite{9152765}!
+It only resumed in 2023 after getting feedbacks from academic 
+community \cite{swiss_evoting_chronik} about the various components used in 
 the electronic voting software. However, it is not an isolated  
@@
 \begin{itemize}
-  \item Cast-as-intended: voters get proof that the electronic ballot accurately reflects their choices.
-  \item Collected-as-cast: the election authority provides proof that the electronic ballots are received without tampering.
-  \item Counted-as-collected: the election authority provides proof that the results are based on correctly counting all received ballots.
+  \item \textit{cast-as-intended}: voters get proof that the electronic ballot accurately reflects their choices.
+  \item \textit{collected-as-cast}: the election authority provides proof that the electronic ballots are received without tampering.
+  \item \textit{counted-as-collected}: the election authority provides proof that the results are based on correctly counting all received ballots.
 \end{itemize}
 
-\noindent 
-Finally, voters or scrutineers inspect these proofs and accept or reject the election results based on 
+Finally, voters and scrutineers inspect these proofs and accept or reject the election results based on 
 the verification of these proofs. In practice, this means that during the execution of an election, 
@@
 once the election has concluded. This ensures that the election process was conducted 
-properly and that the results are accurate, but it is applied during or after the voting has taken place.
-However, can we use it before an election?
-The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
-it, and develop various components of electronic voting 
-software in this formal language. This process is called as  formal verification, or correct-by-construction,
-and it ensures that the software always produces valid proofs, 
-which are consistently accepted by voters and scrutineers. In other words, formal verification
+properly and that the results are accurate, but it is only in action during or after the voting has taken place.
+However, can we use it as a guiding principle to develop an electronic voting software, way before 
+an election? The answer is yes; we can use a formal language to express end-to-end verifiability, or parts of 
+it, and develop various components of an electronic voting 
+software in this formal language. This process is called formal verification, or correct-by-construction,
+and it ensures that the software always produces valid proofs that 
+are accepted by voters and scrutineers every time. In other words, formal verification
 can be employed to develop reliable electronic voting software.
@@
 
-In this paper, we present a certified implementation of sigma protocol --an efficient 
+In this paper, we present a certified implementation of $\Sigma$-protocol --an efficient 
 type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
-the formal language of Coq proof assistant. 
+the formal language of the Coq proof assistant. 
 We have formalised and analysed the interactive version of 
-the Sigma protocol, but in practice it is not convenient due to the required interaction. 
-Therefore, all Sigma protocol implementations use the Fiat-Shamir 
-transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
-using a hash function to replace the randomness of the public-coin verifier, though 
+$\Sigma$-protocol, but in practice it is not convenient due to the required interaction. 
+Therefore, all $\Sigma$-protocol implementations use the \textit{Fiat-Shamir} 
+transformation \cite{10.5555/36664.36676} to make them non-interactive. 
+Fiat-Shamir transformation replaces the randomness of the public-coin verifier by 
+a cryptographic hash function, though 
 some care is required \cite{10.1007/978-3-642-34961-4_38}.
-To make our formalisation self-contained and independent of external libraries, we have 
-encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
-have implemented efficient prime field arithmetic procedures and the Schnorr group to 
-ensure our library is concrete and executable. Finally, we extract WebAssembly and 
+Therefore, we have encoded SHA-256 in Coq, with the usual correctness properties \cite{nist_fips_180_4},
+to make our formalisation self-contained and independent of external libraries. Additionally, we 
+have implemented efficient arithmetic procedures for prime field and the Schnorr group to 
+ensure our library is usable. \textcolor{blue}{Finally, we extract WebAssembly and 
 Rust code from our certified implementation, one of the novelties of our 
-formalisation.
-
-There are numerous implementations of sigma protocol in various languages, 
-e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
+formalisation}.
+
+There are numerous implementations of  $\Sigma$-protocol in various languages, 
+e.g., Helios is written in Python \cite{helios_crypto}, Belenois is written in OCaml \cite{belenios_core}, 
+and SwissPost is written in Java \cite{swisspost_crypto_primitives}.
 However, there are two main issues with these implementations: 
@@
 once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java) and 
-(ii) none of these implementations offer any formal guarantees about the correctness of the code.
-Therefore, we use our formalisation to model the sigma protocol implemented in Helios, 
-Belenois, and SwissPost voting systems to demonstrate the usablity of 
-our library. Unlike Helios and SwissPost,
-we write one implementation and extract WebAssembly (front-end) and Rust (back-end) (\textbf{using the MetaCoq library}).
-Belenois is slightly different in this respect and uses Js\_of\_ocaml 
+ (ii) more importantly, none of these implementations offer any formal guarantees about the code.
+Unlike Helios and SwissPost,
+we write one implementation and extract WebAssembly (front-end) and Rust (back-end) (\textcolor{red}{Todo: using the MetaCoq library}).
+Belenois is slightly different in this respect and uses $Js\_of\_ocaml$ \cite{js_of_ocaml}
 to compile the OCaml code into JavaScript so it has only one 
@@
 and offers no formal guarantees. To the best of our knowledge, 
-this is the firstformal verification of sigma protocol that can be used at 
+this is the first formal verification of sigma protocol that can be used at 
 the front-end (WebAssembly code) and back-end (Rust code).
@@
 \subsection{Outline}
-The rest of the paper is organised as follows: in section \ref{sigma_protocol}
-we explain sigma protocol and its security properties.
+Outline goes here.
 
@@
 Despite the recent growth and popularity of zero-knowledge succinct 
-argument of knowledge (ZKSNARK), sigma protocol remains a
+argument of knowledge (ZKSNARK), $\Sigma$-protocol remains a
 leading cryptographic proof system in privacy-preserving voting systems. 
-Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
+$\Sigma$-protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
 Belenois --used in French elections for overseas 
@@
 SwissPost --used in Swiss elections for overseas voters-- voting 
-systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
+systems \cite{10.1007/978-3-031-15911-4_4} (\textcolor{red}{Look for more examples}). 
 Moreover, recently zero-knowledge proof community started a movement to standardise
@@
 well-understood security.  Other application of sigma protocol 
-include identification schemes, (cite more work).
+include identification schemes, (\textcolor{red}{cite more work}).
 
@@
 $P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
-that ($x$, $w$) $\in$ $R$. To accomplish this, $P$ and $V$ engage in a 
+that ($x$, $w$) $\in$ $R$. To achieve this, $P$ and $V$ engage in a 
 interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
@@
 \section{The Coq Theorem Prover}
-\textbf{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
+\textcolor{red}{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
 can explain MetaCoq here as well and the extraction to Rust and WebAssembly
@@
 
-\section{Related Work, Future Work, and Limitations}
+\section{Related Work, Limitations, and Future Work}
   Given the popularity of sigma protocol in voting 
@@
   butler2021formalising,10.1145/3319535.3354247,287095,almeida2010certifying,10221929,
-  10.1145/3594735}.
-
-  Given the popularity of zero-knowledge in 
-  privacy presearving computation such as voting, cryptocurrencies, 
-  etc., it is not surprising that that sigma protocol and its other 
-  variant (zk-SNARK) are an active area of research
-
-  Given its popularity in voting, it is not surprising that 
-  Sigma protocol is an active area of research \cite{5552642}.
-
-  There are three work. Giles Barthe does not extract to executable code, 
-  CryptoHol uses law of excluded middle, and thomas haines work is more about 
-  verifying a transcript rather than constructing it. Moreover, 
-  it does not reason about probabilities in intuitive way.
-
-\textbf{find the shortcomings of these works}
-Given the importance of sigma protocols in privacy-preserving voting systems,
-it has been formalised before  \cite{5552642,butler2019formalisation,10.1145/3319535.3354247}. 
-\cite{5552642,butler2019formalisation} are mainly focused on establishing the 
-pen-and-paper proofs of sigma protocol into theorem provers and not extracting an executable code.
-On the other hand, \cite{10.1145/3319535.3354247} extract an OCaml code from the Coq 
-formalisation but it is mostly geared towards verifying an Helios election transcript, 
-rather than constructing the primitives to conduct an election. Moreover, 
-it does not reason about probabilities in an intuitive way.
+  10.1145/3594735}. Barthe et al. \cite{5552642}  produced the 
+  first first formalisation of sigma protocol and its composition in 
+  CertiCrypt, a library developed using the Coq theorem prover. 
+  Moreover, their proofs were constructive; however, they 
+  did not extract OCaml code to produce an exectuable. 
+  Butler et al. \cite{ butler2021formalising} has also 
+  formalised sigma protocol in CryptoHOL \cite{10.1007/978-3-662-49498-1_20}, a library 
+  build at the top of Isabelle/HOL. Again, similar to  \cite{5552642}, 
+  their goal is to machine check sigma protcol and commitment schemes 
+  and not extract any executable code. Moreover, Isabellel/HOL admits 
+  law of excluded middle and if it is used in formalisation, 
+  then no executable code can be extractracted. Haines et al. 
+  \cite{287095,10.1145/3319535.3354247} have formalised 
+  sigma protocol in the Coq theorem prover and extracted OCaml code 
+  to verify the 2020 IACR election and SwissPost mix-network. This is 
+  closest to our work; however, their goal is to just verify the 
+  election meanwhile our goal is contruct primitive using 
+  correct-by-construction principal to conduct election. Moreover, 
+  their work lack an intuitive way (probabilistic reasoning) 
+  to reason about zero-knowledge. Firsov et al. \cite{10221929}
+  have formalised sigma protocol in EasyCrypt, successory 
+  of CertiCrypt, but it goal is just machine check 
+  the properties of sigma protocol in EascyCrypt 
+  and not extract an executable code.
+
+  \subsection{Limitation and Future Work}
+   \textbf{Bas: Some text on extraction to Rust and WebAssembly is not verified?}\\
+
+   Our formalisation currently lacks mix-network, a crucial cryptographic primitive used 
+   in electronic voting. A mix-network is used to break the link between the order of 
+   voters and the order of ballots appearing on the election bulletin board. 
+   Specifically, a mix-network takes a list of encrypted ballots as input and 
+   outputs another list of encrypted ballots in a random order.
+   However, since the output is also encrypted, a dishonest mix-network could 
+   potentially drop all the original ballots and manifacture artificial ones to favor a 
+   particular candidate. To prevent such tampering, the mix-network must also 
+   produce a zero-knowledge proof to ensure the correctness of the shuffle \cite{10.1007/978-3-642-02620-1_28,10.1007/978-3-030-51280-4_3}.
+   Given our current infrastructure, it would be fairly straightforward to 
+   encode these algorithms and prove their security properties.
+
+   Another limitation of our work is 
+   that we have formalised the interactive version 
+   of sigma protocol and proved it correctness. However, 
+   in reality the interaction is removed by 
+   using a hash function. Ideally, one would like 
+   to formalise the security of sigma protocol in random oracle 
+   model, the closest we can get. There is a existing 
+   work about formalising random oracle in the Coq theorem 
+   prover \cite{10.1007/11617990_3}; however, it 
+   will still required some non-trivial work.
+
+  In general, voting is a well-defined protocol formalised in terms 
+  message exchanges between a client machine (voter) and a server machine (voting server), 
+  and the cryptographic primitives we developed in this project typically operate on 
+  a client machine (voter) and a server machine (voting server). 
+  However, the correctness of the cryptographic primitives does not imply the 
+  correctness of the whole voting system (protocol). Therefore, we aim to develop 
+  a high-level API for client-server communication, making their interactions explicit 
+  using session types \cite{10.1145/3453483.3454041}. 
+  This approach would provide an end-to-end guarantee for the interaction 
+  between clients and server in the voting system.
 

### 2024-06-10 paper/IEEES/paper.tex
Tmp commit

@@
 \begin{document}
-\title{Hope}
+\title{Bridging Frontend and Backend: Implementing Sigma Protocol in WebAssembly and Rust from a Single Coq Formalisation}
 
@@
   $\Sigma$-protocol remains a popular choice in electronic voting to maintain privacy 
-  and verifiability of elections and still used in prominent e-voting systems such as 
+  and verifiability of elections and still used in prominent electronic voting systems such as 
   Helios, Belenois, SwissPost, etc. However, 
@@
 \subsection{Outline}
-Outline goes here.
+The rest of the paper is organised as follows: in section \ref{sigma_protocol}
+we explain the idea of zero-knowledge proof and sigma protocol. 
+Section \ref{coq_theorem} contains a brief introduction to 
+the Coq theorem prover, MetaCoq, Coq encoding of the Schnorr protocol, 
+uniform probability distribution model, modular arithmetic, Fiat-Shamir transform,
+and reasoning about the complexity of extractor and simulator. 
+In section \ref{case_studies} we show how our library can be used 
+for encoding $\Sigma$-protocol used in Helios, Belenois, and SwissPost. 
+Finally, section \ref{rel_work} concludes the related work, limitation of 
+our work, and future direction.
 
@@
 Despite the recent growth and popularity of zero-knowledge succinct 
-argument of knowledge (ZKSNARK), $\Sigma$-protocol remains a
+argument of knowledge (ZkSNARK), $\Sigma$-protocol remains a
 leading cryptographic proof system in privacy-preserving voting systems. 
@@
 One of the main reasons for its popularity in privacy-preserving voting systems is its
-well-understood security.  Other application of sigma protocol 
-include identification schemes, (\textcolor{red}{cite more work}).
+efficiency and well-understood security.  Other application of sigma protocol 
+include anonymous credentials \cite{10.1145/2660267.2660328}, 
+password-authenticated key exchange \cite{10.5555/2022815.2022838}, 
+signature \cite{10.1007/0-387-34805-0_22}, threshold signature \cite{10.1007/978-3-030-81652-0_2}, 
+etc.
 
@@
 a polynomial-time algorithm that can verify whether a given solution, or witness, to the problem is correct or not.
-More formally, for a given $NP$-relation $R$ and a statement $x$, zero-knowledge proof allows a prover 
+More formally, for a given binary $NP$-relation $R$ and a statement $x$, zero-knowledge proof allows a prover 
 $P$ to convince a verifier $V$ that they posses a witness $w$ --polynomial in length of $x$-- such 
@@
 interactive protocol and  at the end of the protocol $V$ either accepts or rejects the proofs.
-\textit{Sigma protocol}, shown in the figure \ref{fig:sig_picture}, is an efficient three move zero-knowledge proof where the 
+$\Sigma$-protocol --shown in the Figure \ref{fig:sig_picture}-- is an efficient three move zero-knowledge proof where the 
 verifier is assumed to be honest and characterised by completeness, (special) soundness, and 
@@
 if $P$ does not know $w$ for $x$ then it cannot construct a proof 
-(a; c; r) that will passes the verification check. 
+$(a, c, r)$ that will passes the verification check. 
 \item \textbf{Special honest-verifier zero-knowledge proof:}
@@
 and the first efficient sigma protocol was introduced by Schnorr in \cite{schnorr1991efficient}. 
-Eventhough there exists many sigma protocols, the Schnorr protocol is used extensively in privacy-preserving voting systems, e.g, Helios, Belenois, SwissPost, etc. Therefore, 
+Even though there exists many sigma protocols, the Schnorr protocol is used extensively in privacy-preserving voting systems, e.g, Helios, Belenois, SwissPost, etc. Therefore, 
 our formalisation is geared towards the Schnorr protocol. 
-Moreover, we also formalise the composition of (i) $n$ \textit{Parallel} Schnorr, 
-(i) $n$ \textit{And} Schnorr, (iii) $n$ \textit{Or} Schnorr, and (iv) $n$ \textit{Eq} Schnorr protocol. 
+Moreover, we also formalise the composition of (i) $n$ Parallel Schnorr, 
+(i) $n$ And Schnorr, (iii) $n$ Or Schnorr, and (iv) $n$ Eq Schnorr protocol, for an arbitrary natural number $n$. 
 Ideally, given the abstraction of our formlisation (\textit{vector space}), we could have 
@@
 but we decided to focus on the Schnorr protocol and its composition to ensure familiar APIs 
-for e-voting in WebAssembly and Rust. We also formalise Okamoto protocol as a subprotocol 
-for Neq composition (\textbf{Berry: does it sound okay?}). However, we have not seen 
-much use of Neq in the privacy-preserving voting systems, at least in the existing voting systems.
-
-\section{The Coq Theorem Prover}
+for electronic voting in WebAssembly and Rust. We also formalise Okamoto protocol as a sub-protocol 
+for Neq composition (\textcolor{red}{Berry: does it sound okay?}). However, we have not seen 
+much use of Neq in the privacy-preserving voting systems, at least in the existing voting systems 
+such as Helios, Belenois, and SwissPost.
+
+\section{The Coq Theorem Prover}\label{coq_theorem}
 \textcolor{red}{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
@@
 their definitions, and formally prove that the definitions imply the specifications. 
-A user first defines their mathematical object (definition) and then figure 
+A user first defines their mathematical object (definition) and then figures 
 out some true statements (specifications) about 
-that object. Once the user has definition 
-and specifications, they need to prove 
+that object. Once the user has definition and specifications, they need to prove 
 that the definition satisfies the specifications 
@@
 and CloudFlare--, ConCert \cite{10.1145/3372885.3373829}, 
-a smart contract certification framework, etc. \textbf{FIXME: More examples}
+a smart contract certification framework, etc. \textcolor{red}{FIXME: More examples}
 
@@
 Therefore, there is a recent effort to develop more 
-rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
+rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textcolor{red}{FIXME: this is the place 
 to state that we are following this path of MetaCoq and extraction}.
@@
 One possibility is to encode the Coq functions to work with concrete numbers from the underlying group and field, 
-but this leads to cumbersome proofs because of dealing with concrete numbers, but the bigger problem 
-is that it is not modular. For most programming languages, this distinction 
-may not be significant, but it can be a potential source of bugs \cite{10.1007/978-3-662-63958-0_24}. 
+but this leads to cumbersome proofs because we need to deal with the details of concrete numbers during the security proofs. 
+More importantly, it is not modular because it binds the formalisation to multiplicative groups; therefore, 
+it can no longer be used over elliptic curve groups. For most programming languages, this distinction 
+may not be significant, but it can be a potential source of bugs \cite{10.1007/978-3-662-63958-0_24} undermining 
+the security of underlying cryptographic primitives. 
 However, when encoding it in Coq, we need to thoroughly detail these distinctions because 
@@
 Therefore, to avoid this unpleasant situation,  
-we decided to abstract the underlying group as an abstract type $G$, endowed with 
+we abstract the underlying group as an abstract type $G$, endowed with 
 usual group operation, and the underlying field as an abstract type $F$, endowed with 
-filed operation in our formalisation. Moreover, we abstract these two types into a vector space for smooth interaction between 
-group element and field element (exponential needs this). This 
+field operation in our formalisation. 
+Moreover, we abstract these two types into a vector space for smooth interaction between 
+group element and field element (exponentiation in multiplicative group or mulitplication of a field element 
+with a curve point in ellptic curve group is an instance of this interaction). This 
 makes our formalisation generic that can be instantiated with 
@@
 vector space. For example, in our formalisation we have developed 
-efficient algorithm for the Schnorr group but our formalisation can 
+efficient algorithm for the Schnorr (mulitplicative) group but our formalisation can 
 later be also instantiated with elliptic curve group. However, 
@@
 \noindent
- where $F$ is the underlying field, $G$ is the underlying group,
+ $F$ is the underlying field, $G$ is the underlying group,
  $+ : F \rightarrow F \rightarrow F$ is the field addition,
@@
 We prove the completeness and special soundness property of the Schnorr protocol, 
-as shown in Listing \cite{comp_sound}. However, to prove the special honest-verifier 
+as shown in Listing \ref{comp_sound}. However, to prove the special honest-verifier 
 zero-knowledge property we need a model to reason about uniform probability 
@@
 intuitively, we need a model of uniform distribution. 
-We follow the \cite{erwig2006functional}  and 
+We follow \cite{erwig2006functional}  and 
 encode the distribution a list of tuples where the 
-second element of tuple basically is probability of first element 
-in the tuple. Moreover, we define equality on distribution by 
+second element of a tuple is probability --represented as 
+a rational number-- of the first element 
+of the tuple. Moreover, we define equality on distribution by 
 stating that two distributions are equal if they are permutation 
@@
 monad \cite{erwig2006functional} by 
-giving it a suitable definitions of ret and bind. Making 
-it an instance of monad makes our life easier because 
+giving it a suitable definitions of \textit{ret} and 
+\textit{bind}. Making it an instance of monad makes our life easier because 
 we can compose a distribution $d$ $n$ times to 
-returns a distribution on a vector of $n$ elements. 
-However, to reason about cryptographic primitives, we need uniform 
-distribution and therefore we define a function, $uniform\_with\_replacement$, 
+returns a distribution on a vector of $n$ elements, 
+which is needed in proving the special honest-verifier 
+zero-knowledge proof of $n$ composed $\Sigma$-protocol.
+However, we need uniform 
+distribution, rather than an arbitrary distribution, to reason about 
+zero-knowledge of $\Sigma$-protocol, and therefore we define a function, $uniform\_with\_replacement$, 
 to generate uniform distributions, shown in Listing \ref{prob_def}.
-We prove various prop
 
@@
 the simulator distribution $simulator\_distribution$
-that does not involve the secret $x$. 
+that does not involve the secret $x$, shown in Listing \ref{def_zero}. 
 In the Schnorr distibution we draw 
@@
 Using these two definitions, we prove that these two 
-distributions are identical 
-$special\_honest\_verifier\_zkp$. However, 
+distributions are identical $special\_honest\_verifier\_zkp$. However, 
 contrary to the reasoning in cryptographic papers, 
@@
 the first component is a transcript $(a, c, r)$ and 
-the second component is a rational number that represents 
-its probability. The triples in both distrubtions 
+the second component is a rational number, which represents probability of 
+the transcript $(a, c, r)$. The triples in both distrubtions 
 are an accepting transcript (semantic) but they 
@@
 
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
-  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+\begin{lstlisting}[frame=single, language=Coq, caption={Special Honest-Verifier Zero-Knowledge Proof},
+  label={def_zero},captionpos=t, basicstyle=\ttfamily\footnotesize,
   abovecaptionskip=-\medskipamount]
@@
 but we have also formalised a way to combine $n$ And, Or, Eq, 
-and Parallel Schnorr statements. Proving special 
+and Parallel Schnorr statements and proving their special 
 honest-verifier zero-knowledge proof is more challenging 
@@
 is to draw $n$ random element for an uniform distribution 
-and therefore we have written the function $repeat\_dist\_ntimes\_vector$
-that takes a distribution $dist\text{ }A$ and a number $n$ and a returns 
+and therefore we have written the function $repeat\_dist\_ntimes\_vector$ --shown in Listing \ref{dist_comp}--
+that takes a distribution $d$ and a number $n$ and a returns 
 distribution of vectors of length $n$,  encoded as 
@@
 prove that the probability of this distribution 
-is $1/|lf|^n$. We use it 
-in Parallel composition where we combine $n$ sigma protocol and  
-we need to need to draw a vector $n$ random numbers to 
-prove the zero-knowledge property, as shown 
-in $parallel\_schnorr\_distribution$.
-
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
-label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+is $1/|lf|^n$. We use it in Parallel composition where we combine $n$ statments and  
+we need to draw a vector of $n$ random field elements to 
+prove the zero-knowledge property, as shown in $parallel\_schnorr\_distribution$.
+
+\begin{lstlisting}[frame=single, language=Coq, caption={Composition of a Distribution},
+label={dist_comp},captionpos=t, basicstyle=\ttfamily\footnotesize,
 abovecaptionskip=-\medskipamount]
@@
   (uniform_with_replacement lf Hlf) n) ->
-b = mk_prob 1 (Pos.of_nat 
-(Nat.pow (List.length lf) n)).
+b = mk_prob 1 (Nat.pow (List.length lf) n).
 
@@
 \subsection{Efficient Modular Arithmetic}
-As stated earlier, to ensure the ease of proving, we worked with 
-an abstract vector space. However, to execute this code, we need to 
-instantiate the vector space with concrete examples. Therefore, we have 
-encoded a prime field and the Schnorr group \cite{schnorr1991efficient} (mulitplicative 
-group of integers modulo a large prime p) in the Coq theorem prover. 
+As stated earlier, to ensure the ease of proving and modularity, 
+we worked with an (abstract) vector space. However, to execute the code of 
+our formalisation, we need to instantiate the vector space with a concrete entity. 
+Therefore, we have encoded a prime field --shown in Listing \ref{field_def}-- 
+and the Schnorr group \cite{schnorr1991efficient} (mulitplicative 
+group of integers modulo a large prime p) --shown in Listing \ref{group_def}-- in the Coq theorem prover. 
 To encode the Schnorr group, we postulate three integer $k, p, \text{ and } q$. 
@@
 $k = 2$, these primes are called Sophie Germain primes). Finally, 
-we encode the neutral element $one$, the group multiplication $mul\_schnorr\_group$, 
-and the group inverse $inv\_schnorr\_group$. We prove that our encoding 
+we encode the neutral element ($one$), the group multiplication ($mul\_schnorr\_group$), 
+and the group inverse $inv\_schnorr\_group$ and we prove that our encoding 
 of the Schnorr group in Coq is commutative group by making it 
-an instance of the typeclass $schnorr\_comm$, 
-which is an abstract typeclass that bundles the axioms 
+an instance of the typeclass $schnorr\_comm$, which is an abstract typeclass that bundles the axioms 
 of commutative group.
@@
  \begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of the Schnorr Group},
-  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  label={group_def},captionpos=t, basicstyle=\ttfamily\footnotesize,
   abovecaptionskip=-\medskipamount]
@@
     Hb : v ^ q mod p = 1}.
-
-  (* Neutral Element *)
-  Definition one : Schnorr_group.
-    refine 
-      (mk_schnorr 1 one_mod_p 
-      one_pow_mod_q).
-  Defined.
-
-  Definition mul_schnorr_group 
-      (u v : Schnorr_group) : Schnorr_group.
-  (* Proof terms omitted *)
-  Defined.
 
@@
     | mk_schnorr au Hu Hv => mk_schnorr
-        (Z.of_N (Npow_mod (Z.to_N au) 
-        (Z.to_N (p - 2)) (Z.to_N p)))
-        (@inv_schnorr_group_first au Hu)
-        (inv_schnorr_group_second au Hu Hv)
+        (* terms omitted *)
     end).
@@
 \begin{lstlisting}[frame=single, language=Coq, caption={Coq Encoding of Prime Field},
-  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  label={field_def},captionpos=t, basicstyle=\ttfamily\footnotesize,
   abovecaptionskip=-\medskipamount]
@@
 into a vector space instantiating the vector set with 
-the Schnorr group and the scalar set with the prime field. 
+the Schnorr group and the scalar set with the prime field, 
+shown in Listing \ref{vec_space}. 
 However, in order to establish that it is an 
@@
 
-\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
-  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
+\begin{lstlisting}[frame=single, language=Coq, caption={Vector Space Instantiation},
+  label={vec_space},captionpos=t, basicstyle=\ttfamily\footnotesize,
   abovecaptionskip=-\medskipamount]
@@
 
-\subsection{Fiat-Shamir Transform}
+\subsection{Fiat-Shamir Transform.}
  We have formalised the interactive version of sigma protocol. However,
  interaction is not convenient and therefore
- we use Fiat-Shamir transform to make it non-interactive. We use SHA256 
- to turn the interaction to non-interaction but in order to 
- make it a self-contained library and 
- avoid relying on any external library at the front-end (WebAssembly)
- we have encoded the SHA256 in the Coq theorem prover, with usual correctness 
- properties.
-
-\section{Case Studies/Experiment}
+ Fiat-Shamir transform is used to make the sigma protocol non-interactive. 
+ Instead of waiting for a challenge from the verifier, the prover computes 
+ the challenge by hashing the commitment and possibly other public 
+ information by a random oracle.
+ This challenge is now deterministic and can be reproduced by anyone 
+ who knows the commitment and has access to the oracle. 
+ In practical implementations, cryptographic hash functions like SHA-256 are 
+ used in place of a random oracle. The random oracle model (ROM) assumes that these hash functions 
+ behave like a perfect random oracle, meaning their outputs are 
+ indistinguishable from random values and are consistent for any given input.
+ In this formalisation, we have encoded SHA256 we have encoded the SHA256 in the Coq 
+ theorem prover, with usual correctness properties stated in the NIST document \cite{nist_fips_180_4}.
+ Our goal is to make sure that our library is self-contained and does 
+ not depend on any external libraries, which is important specially 
+ for the front-end.
+
+\subsection{Efficient Extractor.}
+
+In this section we explain the ideas behind the formalisation of 
+efficient extractor and simulator. Recall that in $\Sigma$-protocol, 
+the extractor is efficient, i.e., it runs in polynomial time in its input length.
+However, the functions from the vector space does not captures the 
+infomation about complexity of operations, i.e., they do not 
+capture the number of steps they take to compute for a given input. 
+In our formalisation, we found that we could have followed the 
+monadic approach \cite{10.1145/3473585,10.1145/3158124} by adding an extra 
+return value for the number of steps it takes during the 
+execution for a given input for all the functions in vector space. 
+Moreover, monadic approach composes well, i.e., we can take 
+two monadic functions and by composing them together we 
+can compute the complexity of composed function. However, 
+during the code extraction into Rust and WebAssembly, it would 
+have stuck with all the function and destroyed our APIs. 
+Therefore, we decided to take another approach. 
+In practice, an extractor in multiplicative group is 
+a function that can compute the inverse efficiently and 
+in our concrete model we compute inverse using 
+the binary exponentiation function $repeat\_op\_ntimes\_rec$. 
+Therefore, we decided to encode an inductive data type $complexity\_repeat\_op\_ntimes\_rec$ --shown in \ref{extractor_complex}--
+that captures the number of steps of a binary exponentiation 
+fuction. Finally, we proved in theorem $correct\_complexity\_repeat\_op\_ntimes\_rec$ that 
+(concrete) function $repeat\_op\_ntimes\_rec$ runs in logarithmic in its input, or 
+polynomial (linear) in the nubmer of bits of its input. With this method, 
+we do not need to change anything in our API but the downside is that 
+it does not compose well like monadic approach. Nonetheless, it is 
+sufficient for our approach because our main goal is to extract 
+Rust and WebAssembly from our formalisation whose API are closely 
+aligned with a real-world library.
+
+\begin{lstlisting}[frame=single, language=Coq, caption={Extractor Complexity},
+  label={extractor_complex},captionpos=t, basicstyle=\ttfamily\footnotesize,
+  abovecaptionskip=-\medskipamount]
+Inductive complexity_repeat_op_ntimes_rec 
+(e t : N) : positive -> N -> N -> Prop :=
+| xH_case : complexity_repeat_op_ntimes_rec e t xH 
+    (N.modulo e t) N0
+| xO_case p ret w : 
+    complexity_repeat_op_ntimes_rec e t p ret w ->
+    complexity_repeat_op_ntimes_rec e t (xO p) 
+    (N.modulo (ret * ret) t) (N.succ w)
+| xI_case p ret w : 
+    complexity_repeat_op_ntimes_rec e t p ret w ->
+    complexity_repeat_op_ntimes_rec e t (xI p) 
+    (N.modulo (e * (ret * ret)) t) (N.succ w).
+
+Lemma correct_complexity_repeat_op_ntimes_rec : 
+  forall n e w, complexity_repeat_op_ntimes_rec 
+    (repeat_op_ntimes_rec e n w)  (N.log2 n).
+Proof. (* proof terms omitted *) Qed.
+\end{lstlisting}
+
+\section{Case Studies/Experiment}\label{case_studies}
   We use our formalisation to model the Cryptographic protocols implemented in 
@@
 
-\section{Related Work, Limitations, and Future Work}
+\section{Related Work, Limitations, and Future Work}\label{rel_work}
   Given the popularity of sigma protocol in voting 
@@
   \subsection{Limitation and Future Work}
-   \textbf{Bas: Some text on extraction to Rust and WebAssembly is not verified?}\\
+   \textcolor{red}{Bas: Some text on extraction to Rust and WebAssembly is not verified?}
 
@@
    to formalise the security of sigma protocol in random oracle 
-   model, the closest we can get. There is a existing 
+   model, the closest we can get. This means that under the assumption 
+   that the hash function behaves as a random oracle, the non-interactive 
+   proof derived from the Fiat-Shamir transform is secure. 
+   The random oracle model provides a framework where we can 
+   reason about the security properties  of 
+   the transform. There is an existing 
    work about formalising random oracle in the Coq theorem 
-   prover \cite{10.1007/11617990_3}; however, it 
-   will still required some non-trivial work.
+   prover \cite{10.1007/11617990_3} and we would like to 
+   connect it our implementation; however, it 
+   will require some non-trivial work.
 
